---
title: |
  | Supporting Information for:
  | An Interpretable Multilevel Model of Isocratic Retention Explaining Between-Analyte and Between-Column Variability
author:
  - name: "Paweł Wiczling*"
    affiliations:
      - name: "Department of Biopharmaceutics and Pharmacodynamics, Medical University of Gdańsk, Gen. J. Hallera 107, 80-416 Gdańsk, Poland"
date: "`r format(Sys.Date())`"
format:
  pdf:
    pdf-engine: xelatex
    toc: true
    number-sections: true
    colorlinks: true
    fig-width: 7
    fig-height: 7
    keep-tex: true
    template-partials: 
      - title.tex
    include-in-header:
      text: |
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
        \setlength{\tabcolsep}{3pt}
        \usepackage{longtable}
        \usepackage{array}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE, message=FALSE, error=FALSE, warning=FALSE, echo=FALSE, comment=NA, out.width='95%')
```

```{r, include=FALSE}
library(dplyr)
library(kableExtra)

```

{{< pagebreak >}}

# Table S1. Summary of the MCMC simulations of the marginal posterior distributions of population-level model parameters. 

Summary of posterior parameter estimates. The table reports posterior summaries for each parameter, including measures of central tendency (mean, median), uncertainty (standard deviation, median absolute deviation, and 5th/95th percentiles), and MCMC diagnostic statistics (rhat, bulk effective sample size, and tail effective sample size).

```{r summary1}
df <- read.csv("../deliv/tables/manuscript/supplement/parameter-estimates.csv", header = TRUE)    

df %>%
  mutate(across(where(is.numeric), ~ signif(.x, 3)))  %>%
    mutate(across(median:mad, ~ round(.x, 3)))  %>%
  kableExtra::kbl(
    escape = TRUE,
    longtable = TRUE,
    format = "latex"
  ) %>%
  kableExtra::kable_styling(
    latex_options = "repeat_header",
    font_size = 7
  )
```

{{< pagebreak >}}


```{r summary2}
df <- read.csv("../deliv/tables/manuscript/supplement/parameter-estimates-kappa.csv", header = TRUE)    

df %>%
  mutate(across(where(is.numeric), ~ signif(.x, 3)))  %>%
    mutate(across(median:mad, ~ round(.x, 3)))  %>%
  kableExtra::kbl(
    escape = TRUE,
    longtable = TRUE,
    format = "latex"
  ) %>%
  kableExtra::kable_styling(
    latex_options = "repeat_header",
    font_size = 7
  )
```

{{< pagebreak >}}

```{r summary3}
df <- read.csv("../deliv/tables/manuscript/supplement/parameter-estimates-omegad.csv", header = TRUE)    

df %>%
  mutate(across(where(is.numeric), ~ signif(.x, 3)))  %>%
    mutate(across(median:mad, ~ round(.x, 3)))  %>%
  kableExtra::kbl(
    escape = TRUE,
    longtable = TRUE,
    format = "latex"
  ) %>%
  kableExtra::kable_styling(
    latex_options = "repeat_header",
    font_size = 7
  )
```

{{< pagebreak >}}

# Table S2. Column Characteristic

```{r columns}
column_df <- data.frame(
  No = 1:13,
  Phase = c(
    "Agilent 300SB-C3", "Agilent Eclipse XDB-CN", "Agilent SB-Phenyl",
    "Agilent PFP", "Agilent Bonus RP", "Varian/Agilent C18-A",
    "Waters CSH Phenyl-Hexyl", "Waters HSS PFP", "Agilent SB-C8",
    "Waters BEH C8", "Agilent Eclipse PAH", "Agilent Eclipse Plus C18",
    "Agilent SB-C18"
  ),
  PS = c(300, 80, 80, 120, 80, 180, 130, 100, 80, 130, 95, 95, 80),
  Ligand = c(
    "C3", "CN", "phenyl", "PFP", "C14", "C18",
    "phenyl-hexyl", "PFP", "C8", "C8", "C18", "C18", "C18"
  ),
  Endcapping = c(
    "no", "double", "no", "yes", "triple", "yes",
    "yes", "no", "no", "yes", "double", "double", "no"
  ),
  CL = c(3.1, 4.3, 5.5, 5.1, 9.5, 13.8, 14.0, 7.0, 5.5, 13.0, 14.0, 9.0, 10.0),
  `mm x mm, um` = c(
    "12.5 x 2.1, 5", "12.5 x 2.1, 5", "5 x 2.1, 1.8",
    "5 x 2.1, 1.9", "5 x 2.1, 1.8", "10 x 2.0, 3",
    "5 x 2.1, 3.5", "5 x 2.1, 3.5", "5 x 2.1, 2.7",
    "5 x 2.1, 1.7", "5 x 2.1, 1.8", "5 x 2.1, 1.8",
    "5 x 2.1, 1.8"
  ),
  Other = c(
    "Diisopropyl silane", "Dense bonding", "Diisopropyl silane",
    "Superficially porous", "Diisopropyl silane Embedded amide",
    "Polar modified", "Low silanol activity", "High silanol activity",
    "Diisopropyl silane", "Low silanol activity", "Polymeric",
    "Dense monolayer", "Diisobutyl silane"),
  Abbr. = c(
    "300SB-C3", "Eclipse XDB-CN", "SB-Phenyl", "PFP",
    "Bonus RP", "C18-A", "CSH Phenyl-Hexyl", "HSS PFP",
    "SB-C8", "BEH C8", "Eclipse PAH", "Eclipse Plus C18",
    "SB-C18"
  ),
  stringsAsFactors = FALSE
)

column_df %>%
  kableExtra::kbl(
    escape = TRUE,
    format = "latex",
    booktabs = TRUE,
  ) %>%
  kableExtra::kable_styling(
    font_size = 7,
     latex_options = "HOLD_position"
  )%>%
  kableExtra::column_spec(8, width = "2.0cm") %>%   # Other
  kableExtra::column_spec(9, width = "2.0cm") %>%   # Other
  kableExtra::column_spec(2, width = "2.0cm") %>%   # Other
  footnote(
    general = "CL: carbon loading, PS: Pore Size"
  )
```

# Figure S1. Raw data.

![](../deliv/figures/manuscript/supplement/raw-data.pdf)
{{< pagebreak >}}

# Figure S2. Utility function. 

$$
\begin{aligned}
d &= \left| \log k_1 - \log k_2 \right|, \\
l_o &= 10^{\min\left(\log k_1,\ \log k_2\right)}, \\
h_i &= 10^{\max\left(\log k_1,\ \log k_2\right)}, \\
U &=
\frac{1}{1 + e^{-(d - 0.07918125)/0.015}}
\times
\frac{1}{1 + e^{-(l_o - 2)/0.25}}
\times
\frac{1}{1 + e^{-(10 - h_i)/1.5}}.
\end{aligned}
$$

![](../deliv/figures/manuscript/supplement/utylity-1.pdf)
{{< pagebreak >}}

# Figure S3. Residuals

![](../deliv/figures/manuscript/supplement/residuals.pdf)
{{< pagebreak >}}

# Figure S4. GOF plots for 6 analytes

![](../deliv/figures/manuscript/supplement/analyte-fits-example.pdf)
{{< pagebreak >}}

# Figure S5. Etas

eta~a~ represents the deviation of an individual analyte’s parameter from its expected population-level value for a typical column, assuming no interactions.

![](../deliv/figures/manuscript/supplement/etas.pdf)
{{< pagebreak >}}

# Figure S6. Kappas

kappa~c~ represents the deviation of an individual analyte’s parameter from its expected population-level value for a typical analyte, assuming no interactions. The numbers correspond to specific columns (stationary phases). The legend is provided in Table 2S.

![](../deliv/figures/manuscript/supplement/kappas-1.pdf)
{{< pagebreak >}}
![](../deliv/figures/manuscript/supplement/kappas-2.pdf)
{{< pagebreak >}}

# Figure S7. Dzetas

dzeta~a,c~ represents analyte-column interactions.

![](../deliv/figures/manuscript/supplement/dzeta-1.pdf)
{{< pagebreak >}}
![](../deliv/figures/manuscript/supplement/dzeta-2.pdf)
{{< pagebreak >}}
![](../deliv/figures/manuscript/supplement/dzeta-3.pdf)
{{< pagebreak >}}
![](../deliv/figures/manuscript/supplement/dzeta-4.pdf)
{{< pagebreak >}}
![](../deliv/figures/manuscript/supplement/dzeta-5.pdf)
{{< pagebreak >}}
![](../deliv/figures/manuscript/supplement/dzeta-6.pdf)
{{< pagebreak >}}
![](../deliv/figures/manuscript/supplement/dzeta-7.pdf)
{{< pagebreak >}}
![](../deliv/figures/manuscript/supplement/dzeta-8.pdf)
{{< pagebreak >}}
![](../deliv/figures/manuscript/supplement/dzeta-9.pdf)
{{< pagebreak >}}
![](../deliv/figures/manuscript/supplement/dzeta-10.pdf)
{{< pagebreak >}}
![](../deliv/figures/manuscript/supplement/dzeta-11.pdf)
{{< pagebreak >}}
![](../deliv/figures/manuscript/supplement/dzeta-12.pdf)
{{< pagebreak >}}
![](../deliv/figures/manuscript/supplement/dzeta-13.pdf)
{{< pagebreak >}}




# Licenses {.unnumbered}

-   Code & copy; 2023, Paweł Wiczling, licensed under BSD-3.
-   Text & copy; 2023, Paweł Wiczling, licensed under CC-BY-NC 4.0.

# Original Computing Environment {.unnumbered}

```{r}
sessionInfo()
```
