---
title: "Model 107. Izocratic Mulitilevel Model with Dewetting, Silanol and pKa effects"
author:
  - name: "Paweł Wiczling*"
    affiliations:
      - name: "Department of Biopharmaceutics and Pharmacodynamics, Medical University of Gdańsk, Gen. J. Hallera 107, 80-416 Gdańsk, Poland"
date: "`r format(Sys.Date())`"
format:
  html:
    theme: cosmo
    toc: true
    code-fold: true  
    code-tools: true
    fig-width: 7
    fig-height: 7
knitr:
  opts_chunk: 
    dev: "ragg_png"
---

# Introductions

In this study, I propose an isocratic multilevel model that accounts for dewetting, silanol interactions, and pKa effects. The model is developed using a dataset available at [link](https://chemrxiv.org/engage/chemrxiv/article-details/64948c82a2c387fa9ac5c1ce), which includes RP-HPLC retention time measurements for 85 analytes (including several duplicates) across 13 columns.

# Setup
```{r setup, message=FALSE}
knitr::opts_chunk$set(cache=FALSE, message=FALSE, error=FALSE, warning=FALSE, comment=NA, out.width='95%')

suppressWarnings(library(dplyr))
suppressWarnings(library(ggplot2))
suppressWarnings(library(patchwork))
suppressWarnings(library(gridExtra))
suppressWarnings(library(naniar))
suppressWarnings(library(knitr))
suppressWarnings(library(data.table))
suppressWarnings(library(tidyverse))
suppressWarnings(library(whisker))
suppressWarnings(library(here))
suppressWarnings(library(cmdstanr))
suppressWarnings(library(posterior))
suppressWarnings(library(bayesplot))
suppressWarnings(library(tidybayes))
suppressWarnings(library(reshape2))
suppressWarnings(library(mrgmisc))
suppressWarnings(library(pracma))
suppressWarnings(library(GGally))
suppressWarnings(library(matrixStats))
suppressWarnings(library(parallel))
suppressWarnings(library(R.utils))
#remotes::install_github("metrumresearchgroup/mrgmisc")
set_cmdstan_path("C:/Users/GUMed/.cmdstan/cmdstan-2.38.0")
select<-dplyr::select
filter<-dplyr::filter
set.seed(10271998) 
source("helper-functions-v100.R")
```

```{r settings}
data_dir = here::here("data")
model_dir <- here::here("model","stan")  
figures_dir <- here::here("deliv","figures", "stan")
tables_dir <- here::here("deliv","tables", "stan")
if(!file.exists(figures_dir)) dir.create(figures_dir, recursive = T)
if(!file.exists(model_dir)) dir.create(model_dir, recursive = T)
if(!file.exists(tables_dir)) dir.create(tables_dir, recursive = T)

data_deriv_dir = here::here("data","deriv")
if(!file.exists(data_deriv_dir)) dir.create(data_deriv_dir, recursive = T)

figures_eda_dir <- here::here("deliv","figures", "stan")
tables_eda_dir <- here::here("deliv","tables", "stan")
if(!file.exists(figures_eda_dir)) dir.create(figures_eda_dir, recursive = T)
if(!file.exists(tables_eda_dir)) dir.create(tables_eda_dir, recursive = T)
```

## Load data
```{r load-data, message=FALSE, warning=FALSE}
dataall <- read.csv(here(data_deriv_dir, "data.csv"), header = TRUE)%>%
  mutate(Compound = HSM3_Name) %>%
  mutate(fi = phi/100,
         logk = log10(k))%>%
  filter(!is.na(logk)) %>%
  group_by(fi, Compound, Column_Phase) %>%
  summarise(logk = mean(logk)) %>%
  ungroup()%>%
   mutate(ID = match(Compound, unique(Compound)),
         column = match(Column_Phase, unique(Column_Phase)))

analytes_names = dataall%>%distinct(ID, .keep_all = T)%>%select(ID, Compound)
column_names = dataall%>%distinct(column, .keep_all = T)%>%select(column,Column_Phase)

smiles <- read.csv(here(data_deriv_dir,"smiles.csv"), sep = ",", header = TRUE)%>%
  select(-ID)%>%
  left_join(analytes_names)%>%arrange(ID)%>%distinct(ID, .keep_all = T)

fg_df = read.csv(file = here(data_deriv_dir,"smarts_functional_groups.csv"), header = TRUE)%>%
  select(-id1,-id2) %>%
  rename(smiles=SMILES) %>%
  left_join(smiles,)%>%arrange(ID)%>%distinct(ID, .keep_all = T)

descriptor_df <- read.csv(file = here(data_deriv_dir,"descriptor_df.csv"), header = TRUE)%>%
  rename(smiles=SMILES) %>%
  left_join(smiles) %>%arrange(ID)%>%distinct(ID, .keep_all = T)

column_df = read.csv(file = here(data_deriv_dir,"columns.csv"), header = TRUE)%>%
  mutate(Column_Phase = str_remove(Phase, "Waters|Agilent"))%>%
  mutate(Column_Phase = str_remove(Column_Phase, " "))%>%
  mutate(Column_Phase = case_when(Column_Phase == "Varian/C18-A" ~ "C18-A",
                                  Column_Phase == "CSH Phenyl- Hexyl"~"CSH Phenyl-Hexyl",
                                 .default = Column_Phase)) %>%
  left_join(column_names) %>%
  rename("carbon_loading" = "Carbon.Loading....",
         "Endcapping" = "Endcapping...."
         ) %>%
  arrange(column)


cation_names = c("Primary_arom_amine",
"Secondary_arom_amine",
"Secondary_aliph_amine",
"Tertiary_aliph_amine",
"Quaternary_aliph_ammonium",
"Secondary_mixed_amine",
"Tertiary_mixed_amine",
"X1.2.Aminoalcohol",
"Hetero_N_basic_H",
"Hetero_N_basic_no_H")

analytes_df = read.csv(file = here(data_deriv_dir,"analytes.csv"), header = TRUE) %>%
   mutate(charge = if_else(pKa..base.d>3.2, 1, 0)) %>%
      mutate(charge =if_else(is.na(charge), 0, charge))
```


## Prepare data
```{r prepare-data, message=FALSE, warning=FALSE}
# Only neutral
fg_df <- fg_df %>% mutate(ID = match(ID, unique(ID)))
dataall <- dataall %>% mutate(ID = match(ID, unique(ID)))
analytes_names <- analytes_names %>% mutate(ID = match(ID, unique(ID)))
smiles <-smiles %>% mutate(ID = match(ID, unique(ID)))
descriptor_df <- descriptor_df %>% mutate(ID = match(ID, unique(ID)))
analytes_df  <- analytes_df %>% mutate(ID = match(ID, unique(ID)))

functional_groups = fg_df%>%select(where(~ is.character(.) || !all(. == 0, na.rm = TRUE))) %>%
   select(-smiles, -Anion, -Kation, -Compound )
 functional_groups_names<- colnames(functional_groups)
 totalnrgroups <- summarise_each(functional_groups, funs(sum))
 
```

## Initial estimates
```{r initial-estimates}
init_aprox <- dataall %>%
  group_by(Compound, ID, column) %>%
  summarise(
    S1 = if_else(n() == 1,-16,polyfit(fi / (1 + 2 * fi), logk, 1)[1]),
    logkw = if_else(n() == 1,polyfit(-16 * fi / (1 + 2 * fi), logk, 0), 
                             polyfit(fi / (1 + 2 * fi), logk, 1)[2]),
    S2 = 2) %>%
  ungroup() %>%
  select(Compound, ID, column, logkw, S2, S1) %>%
  mutate(S1 = -S1 / (1 + 2))

init_vector <- init_aprox %>%
  pivot_longer(cols = c(logkw, S1), names_to = "variable", values_to = "value") %>%
  select(-Compound) %>%
  mutate(variable = case_when(variable=="logkw" ~ "1", 
                              variable=="S1" ~ "2")) %>%
  arrange(variable, column, ID) %>%
  group_by(ID, variable) %>%
  summarize(value = mean(value)) %>%
  group_by(variable) %>%
  mutate(mvalue = mean(value),
         svalue = sd(value)) %>%
  ungroup() %>%
  mutate(value = (value-mvalue)/svalue) %>%
  arrange(variable, ID)
```


```{r set-theme, include = FALSE}
theme_set(theme_bw())
theme_update(
  axis.title = element_text(size = 10, face = "bold"), 
  axis.text = element_text(size = 8), 
  legend.title = element_blank(),
  legend.text = element_text(size = 8),
  legend.key.size = unit(0.4, "cm"),
  strip.text = element_text(size = 8),
  legend.position = "bottom",
  panel.grid.minor = element_blank()
)
```

# Data analysis

# Stan

Multilevel modeling was performed in [Stan software](https://mc-stan.org/) linked with R/ [cmdstanr](https://mc-stan.org/cmdstanr/). For the inference we used 500 iterations, 1000 warmup iterations, and 8 Markov chains. The reduce_sum function was selected to accelerate the calculations. It works by parallelizing the execution of a single Stan chain across multiple cores. Convergence diagnostics were checked using Gelman−Rubin statistics and trace plots.

## Initialize variables and parameters

```{r stan-setup}
data <- dataall %>% arrange(ID,column,fi)

pKa = analytes_df$pKa..base.d

pKa[is.na(pKa)] = -3
pKa[pKa==100] = 10

pHmpKa = 3.2-pKa

nAnalytes=length(unique(data$ID))
nColumns=length(unique(data$column))
datastruct <- with(data,
                  list(nAnalytes=length(unique(data$ID)),
                       nColumns=length(unique(data$column)),
                       nObs=length(data$ID),
                       analyte=match(data$ID, unique(data$ID)),
                       column=match(data$column, unique(data$column)),
                       fi=data$fi,
                       logP=descriptor_df$LogP,
                       logCL=log10(column_df$carbon_loading),
                       dissociated = analytes_df$charge,
                       pHmpKa = pHmpKa,
                       logkobs=logk,
                       run_estimation=1))
```

# Decision making

```{r mod-settings}
model_name <- "mod107"

modelsim_name <- paste0(model_name,"sim")
modelsim_name_ext <- paste0(modelsim_name,".stan")
modsim_model_dir   <- here::here("model", "stan", modelsim_name)
modsim_output_dir   <- here::here("model", "stan", modelsim_name, "output")

if (!file.exists(modsim_model_dir)) dir.create(modsim_model_dir)
if (!file.exists(modsim_output_dir)) dir.create(modsim_output_dir)

modelsimgq_name <- paste0(model_name,"simgq")
modelsimgq_name_ext <- paste0(modelsimgq_name,".stan")
modsimgq_model_dir   <- here::here("model", "stan", modelsimgq_name)
modsimgq_output_dir   <- here::here("model", "stan", modelsimgq_name, "output")

if (!file.exists(modsimgq_model_dir)) dir.create(modsimgq_model_dir)
if (!file.exists(modsimgq_output_dir)) dir.create(modsimgq_output_dir)

modelsimdm_name <- paste0(model_name,"dm")
modelsimdm_name_ext <- paste0(modelsimdm_name,".stan")
modsimdm_model_dir   <- here::here("model", "stan", modelsimdm_name)
modsimdm_output_dir   <- here::here("model", "stan", modelsimdm_name, "output")

if (!file.exists(modsimdm_model_dir)) dir.create(modsimdm_model_dir)
if (!file.exists(modsimdm_output_dir)) dir.create(modsimdm_output_dir)
```

## Model
```{r sim, eval=T}
mod107sim <- cmdstan_model(here(modsim_model_dir,modelsim_name_ext))
```

## Helper functions
```{r helper-function}
utility_fn <- function(param_draws, fi_new) {
param_draws %>%
  tidybayes::spread_draws(param[i,c,..]) %>%
   pivot_wider(
    id_cols = c(.draw,c),
    names_from = i,
    values_from = starts_with("param")) %>%
  tidyr::expand_grid(fi = fi_new) %>%
  mutate(logk1 = funlogki_pKa_v102(param.1_1, param.2_1, param.3_1,
                                   param.4_1, param.5_1, param.6_1,
                                   param.7_1, param.8_1, param.9_1,
                                   param.10_1,fi)) %>%
  mutate(logk2 = funlogki_pKa_v102(param.1_2, param.2_2, param.3_2,
                                   param.4_2, param.5_2, param.6_2,
                                   param.7_2, param.8_2, param.9_2,
                                   param.10_2,fi)) %>%
    mutate(
    d  = abs(logk1 - logk2),
    lo = 10^(pmin(logk1, logk2)),
    hi = 10^(pmax(logk1, logk2)), # midpoint for selectivity of 1.2, zero for 1.04 and 1 for 1.5
    utylity = plogis((d-0.07918125)/0.015)*plogis((lo-2)/0.25)*plogis((10-hi)/1.5)) %>%
    select(fi, c, utylity)
}

expected_utility <- function(draws, fi_new) {
  utility_fn(draws,fi_new) %>%
  group_by(c, fi) %>%
  summarize(prob = mean(utylity)) %>% ungroup()
}


safe_worker <- function(m,  .stanmodel = stanmodel, 
                            .datastruct_sim  = datastruct_sim, 
                            .logkobs_sim_exp = logkobs_sim_exp,
                            .current_best = current_best) {

    logkobsi              = .logkobs_sim_exp %>% dplyr::filter(draw == m)
    datastruct_sim_update = .datastruct_sim
    datastruct_sim_update$nObs_sim = datastruct_sim_update$nObs_sim + length(logkobsi$n_logkobs)
    datastruct_sim_update$logkobs_sim = c(datastruct_sim_update$logkobs_sim, logkobsi$n_logkobs)
    datastruct_sim_update$fi_sim = c(datastruct_sim_update$fi_sim, logkobsi$n_fi)
    datastruct_sim_update$analyte_sim = c(datastruct_sim_update$analyte_sim, logkobsi$n_analyte)
    datastruct_sim_update$column_sim = c(datastruct_sim_update$column_sim, logkobsi$n_column)
  
 tryCatch({
   
    # fit_mode <- mod107sim$optimize(
    #   data = datastruct_sim_update,
    #   init = init_sim,
    #   output_dir = modsimgq_output_dir,
    #   output_basename = paste0("-o-", m),
    #   jacobian = TRUE
    # )
    # 
    # fit_updated <- mod107sim$laplace(
    #   data = datastruct_sim_update,
    #   output_dir = modsimgq_output_dir,
    #   output_basename = paste0("-l-", m),
    #   mode = fit_mode
    # )

   fit_updated <- .stanmodel$sample(
   data = datastruct_sim_update,
   output_dir = modsimgq_output_dir,
   output_basename = paste0("-temp-", m),
   init = init_sim,
   iter_warmup = 500,
   iter_sampling = 1000,
   chains = 1,
   parallel_chains = 1,
   refresh = 100,
   show_messages = FALSE,
   adapt_delta=0.95
 )

  param_updated       <- fit_updated$draws("param")
  exp_utility_updated <- expected_utility(param_updated, seq(0, 1, 0.05))
  updated_best        <- max(exp_utility_updated$prob)

  gains <- updated_best - .current_best
  gains
       
 }, error = function(e) {
    message(sprintf("Simulation %s (iter %s) failed: %s", m, indx_new, e$message))
   gains = NULL
  })
  }
  

  
compute_evsi_parralel = function(i_exp, .stanmodel       = stanmodel, 
                                           .datastruct_sim  = datastruct_sim,
                                           .logkobs_sim = logkobs_sim, 
                                           .current_best = current_best,
                                           .n_future = 100) {
  print(i_exp)
  logkobs_sim_exp = .logkobs_sim %>% filter(n_exp == i_exp)
  
  gains_list <- bettermc::mclapply(
    1:.n_future,
    \(x) safe_worker(x, .stanmodel = .stanmodel, 
                        .datastruct_sim  = .datastruct_sim, 
                        .logkobs_sim_exp = logkobs_sim_exp,
                        .current_best = .current_best),
    mc.cores = max(1, detectCores()-4),
    mc.set.seed = TRUE,
    mc.preschedule = FALSE, mc.allow.fatal = NULL,
    mc.timeout.elapsed = 180, mc.force.fork = TRUE,
    mc.retry = 2
  )
  
  print(unlist(Filter(Negate(is.null), gains_list)))
  evsi <- mean(unlist(Filter(Negate(is.null), gains_list)),na.rm = TRUE)
  evsi
}


plotting_i = function(df, .column_names = column_names, .analyte_names = analyte_names) {
  df%>%
  tidybayes::spread_draws(param[i,c,..])%>%
  rename(column=c) %>%
  left_join(.column_names)%>%
  tidyr::expand_grid(fi = seq(0.0,1,0.05)) %>%
  mutate(logk1 = funlogki_pKa_v102(param.1,
                                   param.2,
                                   param.3,
                                   param.4,
                                   param.5,
                                   param.6,
                                   param.7,
                                   param.8,
                                   param.9,
                                   param.10,fi)) %>%
  ggplot(aes(x = fi, y = logk1, color = as.factor(i),fill = as.factor(i))) +
  ggdist::stat_lineribbon(.width = c(.90), alpha = 1/2) +
  labs(x="\u03C6", y="logk") +
  facet_wrap(.~Column_Phase)+
  coord_cartesian(ylim=c(log10(2),log10(10)))
}
```

## Case 1. Aceclofenac and Trans-chalcone and CSH Phenyl-Hexyl Phase
### Perfect
```{r dataset-perfect-case1}
datastruct_sim = datastruct;
idx = c(68,72)
temp_data = dataall%>%filter(ID%in% idx)
temp_data$i = match(temp_data$ID, unique(temp_data$ID))
pKa = analytes_df %>% filter(ID %in% idx) %>% pull(pKa..base.d) %>% replace(is.na(.), -3) %>% replace(. == 100, 10)
pHmpKa = 3.2 - pKa
logP = descriptor_df%>% filter(ID%in% idx) %>% pull(LogP)

nAnalytes_sim = length(unique(temp_data$ID))
nObs_sim = length(temp_data$ID)
datastruct_sim$nAnalytes_sim=nAnalytes_sim;
datastruct_sim$nObs_sim= nObs_sim;
datastruct_sim$logkobs_sim= temp_data$logk;
datastruct_sim$fi_sim = temp_data$fi;
datastruct_sim$logP_sim= logP;
datastruct_sim$pHmpKa_sim= pHmpKa;
datastruct_sim$analyte_sim= match(temp_data$ID, unique(temp_data$ID));
datastruct_sim$column_sim= match(temp_data$column, unique(data$column));

init_sim <- function(){
  list( etaStd  = t(matrix(rep(0,nAnalytes_sim*3), nrow=nAnalytes_sim)),
        dzeta1  = matrix(rep(0,nColumns*nAnalytes_sim), nrow=nAnalytes_sim),
        dzeta2  = matrix(rep(0,nColumns*nAnalytes_sim), nrow=nAnalytes_sim),
        dzeta3  = matrix(rep(0,nColumns*nAnalytes_sim), nrow=nAnalytes_sim))
}
```

```{r run-perfect-case1, eval=F}
fit_opt_perfect <- mod107sim$optimize(
  data = datastruct_sim,
  output_dir = modsim_output_dir,
  output_basename =  paste0(modelsim_name, "-opt-perfect-case1"),
  init =  init_sim,
  jacobian=TRUE)

fit_lap_perfect <- mod107sim$laplace(
  data = datastruct_sim,
  mode = fit_opt_perfect,
  output_dir = modsim_output_dir,
  output_basename = paste0(modelsim_name, "-lap-perfect-case1"))

fit_sam_perfect <- mod107sim$sample(
   data = datastruct_sim,
   output_dir = modsim_output_dir,
   output_basename =  paste0(modelsim_name, "-sam-perfect-case1"),
   init = init_sim,
   iter_warmup = 500,
   iter_sampling = 500,
   chains = 4,
   parallel_chains = 4,
   refresh = 100,
   adapt_delta=0.95
 )
```

```{r read-perfect-case1}
fit_sam_perfect <- cmdstanr::as_cmdstan_fit(c(
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-perfect-case1"), "-1.csv"),
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-perfect-case1"), "-2.csv"),
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-perfect-case1"), "-3.csv"),
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-perfect-case1"), "-4.csv")))
draw_sam_perfect <-fit_sam_perfect$draws("param") 

# fit_lap_perfect <- cmdstanr::as_cmdstan_fit(c(paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-lap-perfect-case1"), "-1.csv")))
# draw_lap_perfect <-fit_lap_perfect$draws("param") 

plotting_i(draw_sam_perfect)
#plotting_i(draw_lap_perfect)
```

### Single column data
```{r data-scolumn-case1}
datastruct_sim_case1 = datastruct;
idx = c(68,72)
temp_data = dataall%>%filter(column==7, ID%in% idx)
temp_data$i = match(temp_data$ID, unique(temp_data$ID))
temp_data_all = dataall%>%filter(ID%in% idx)
temp_data_all$i = match(temp_data_all$ID, unique(temp_data_all$ID))
pKa = analytes_df %>%
  filter(ID %in% idx) %>%
  pull(pKa..base.d) %>%
  replace(is.na(.), -3) %>%
  replace(. == 100, 10)
pHmpKa <- 3.2 - pKa
logP = descriptor_df%>% filter(ID%in% idx) %>% pull(LogP)
nAnalytes_sim = length(unique(temp_data$ID))
nObs_sim = length(temp_data$ID)
datastruct_sim_case1$nAnalytes_sim=nAnalytes_sim;
datastruct_sim_case1$nObs_sim= nObs_sim;
datastruct_sim_case1$logkobs_sim= temp_data$logk;
datastruct_sim_case1$fi_sim = temp_data$fi;
datastruct_sim_case1$logP_sim= logP;
datastruct_sim_case1$pHmpKa_sim= pHmpKa;
datastruct_sim_case1$analyte_sim= match(temp_data$ID, unique(temp_data$ID));
datastruct_sim_case1$column_sim= match(temp_data$column, unique(data$column));
```

```{r run-scolumn-case1, eval=F}
fit_opt_scolumn <- mod107sim$optimize(
  data = datastruct_sim_case1,
  output_dir = modsim_output_dir,
  output_basename =  paste0(modelsim_name, "-opt-scolumn-case1"),
  init =  init_sim,
  jacobian=TRUE)

fit_lap_scolumn <- mod107sim$laplace(
  data = datastruct_sim_case1,
  mode = fit_opt_scolumn,
  output_dir = modsim_output_dir,
  output_basename = paste0(modelsim_name, "-lap-scolumn-case1"))

fit_sam_scolumn <- mod107sim$sample(
   data = datastruct_sim_case1,
   output_dir = modsim_output_dir,
   output_basename =  paste0(modelsim_name, "-sam-scolumn-case1"),
   init = init_sim,
   iter_warmup = 500,
   iter_sampling = 500,
   chains = 4,
   parallel_chains = 4,
   refresh = 100,
   adapt_delta=0.95
 )
```

```{r read-scolumn-case1}
fit_sam_scolumn <- cmdstanr::as_cmdstan_fit(c(
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-scolumn-case1"), "-1.csv"),
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-scolumn-case1"), "-2.csv"),
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-scolumn-case1"), "-3.csv"),
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-scolumn-case1"), "-4.csv")))
draw_sam_scolumn <-fit_sam_scolumn$draws("param") 

fit_lap_scolumn <- cmdstanr::as_cmdstan_fit(c(paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-lap-scolumn-case1"), "-1.csv")))
draw_lap_scolumn <-fit_lap_scolumn$draws("param") 

plotting_i(draw_sam_scolumn)
#plotting_i(draw_lap_scolumn)
```

### Simulate future observations
```{r simulate-kobs-case1}
datastruct_sim_gq_case1=datastruct_sim_case1
datastruct_sim_gq_case1$fi_sim_new = rep(seq(0,1,0.05),13);
datastruct_sim_gq_case1$column_sim_new = rep(seq(1,13,1),21);
datastruct_sim_gq_case1$K=length(datastruct_sim_gq_case1$fi_sim_new);

mod107simgq <- cmdstan_model(here(modsimgq_model_dir, modelsimgq_name_ext))

fit107simgq  <- mod107simgq$generate_quantities(fit_sam_scolumn,
                                          data = datastruct_sim_gq_case1,
                                          seed = 123,
                                          parallel_chains = 4,
                                          output_dir = modsimgq_output_dir,
                                          output_basename = paste0(modelsimgq_name, "-sam-scolumn-case1"))

set.seed(2026)
logkobs_future_case1 = fit107simgq$draws(c("n_logkobs","n_fi","n_column")) %>% 
  as_draws_df()%>%
  slice_sample(n=192)  %>%
  tidybayes::spread_draws(n_logkobs[n_exp,n_analyte],n_fi[n_exp],n_column[n_exp]) %>%
  mutate(draw = match(.draw, unique(.draw))) %>%
   select(-c(.iteration, .chain, .draw))

logkobs_future_case1%>%
 rename(column=n_column) %>%
  left_join(column_names)%>%
  ggplot(aes(x = n_fi, y = n_logkobs, color = as.factor(n_analyte),fill = as.factor(n_analyte))) +
  ggdist::stat_lineribbon(.width = c(.90), alpha = 1/2) +
  labs(x="\u03C6", y="logk") +
  facet_wrap(.~Column_Phase)+
  coord_cartesian(ylim=c(log10(2),log10(10)))
```

### Current expected utility
```{r current-expected-utility-case1}
current_EU_sam_case1 <- expected_utility(draw_sam_scolumn, seq(0,1,0.05)) %>% mutate(type = "current")
#current_EU_lap_case1 <- expected_utility(draw_lap_scolumn, seq(0,1,0.05)) %>% mutate(type = "current (laplace)")
perfect_EU_sam_case1 <- expected_utility(draw_sam_perfect, seq(0,1,0.05)) %>% mutate(type = "perfect")
#perfect_EU_lap_case1 <- expected_utility(draw_lap_perfect, seq(0,1,0.05)) %>% mutate(type = "perfect (laplace)")

current_best_case1 = max(current_EU_sam_case1$prob)
selected_exp_case1 = current_EU_sam_case1 %>% mutate(n_exp=1:n())%>% filter(prob>=0)

#save for trytonp
x_candidates_case1<-selected_exp_case1$n_exp
saveRDS(
  list(
    datastruct_sim = datastruct_sim_case1,
    logkobs_future = logkobs_future_case1,
    current_best = current_best_case1,
    x_candidates = x_candidates_case1,
    case_names = "case1"
  ),
  file = here::here(modsimdm_model_dir, "input_data.rds")
)

p1 <- rbind(current_EU_sam_case1,perfect_EU_sam_case1) %>%
  rename(column=c) %>%
  left_join(column_names) %>%
  ggplot(aes(x = fi, y = prob, color = type)) +
  geom_line()+
  geom_hline(yintercept = c(0.5), color = "darkred",linetype = "dotted")+
  facet_wrap(.~Column_Phase)+
  labs(x="\u03C6", y="E(Utylity)", color = "Phase") +
  coord_cartesian(ylim=c(0, 1)) 

p1
```

### The expected value of sample information (EVSI) 
```{r, evsi-parallel-case1, eval = FALSE}
x_candidates_case1<-selected_exp_case1$n_exp
evsi_values_case1 <- sapply(x_candidates, \(x) compute_evsi_parralel(x, 
                                                                     .stanmodel= mod107sim,
                                                                     .datastruct_sim =datastruct_sim_case1, 
                                                                     .logkobs_sim = logkobs_future_case1, 
                                                                     .current_best = current_best_case1,
                                                                     .n_future = 20))
  
best_case1 <- x_candidates_case1[which.max(evsi_values_case1)]
```

```{r evsi-parallel-tryton-case1, eval = FALSE}
files <- list.files(
  here(modsimdm_output_dir,"case1"),
  pattern = "^evsi_.*\\.rds$",
  full.names = TRUE
)

# read all files into dataframe
evsi_df <- map_dfr(files, \(f) {
  evsi <- readRDS(f)
  task_id <- str_extract(basename(f), "\\d+") |>as.integer()
  tibble(task_id = task_id,evsi = evsi)
})

evsi_df <- tibble(evsi=evsi_df$evsi,
                  n_exp=evsi_df$task_id,
                  fi = datastruct_sim_gq_case1$fi_sim_new,
                  c = datastruct_sim_gq_case1$column_sim_new) %>% 
  left_join(selected_exp_case1) %>%
  select("n_exp", "c", "fi","prob", "evsi", "type")

write.csv(evsi_df, here(modsimdm_model_dir, "evsi-values-sample-case1.csv"))
```

```{r evsi-plot}
evsi_values_case1<-read.csv(here(modsimdm_model_dir, "evsi-values-sample-case1.csv"))

p1 <- evsi_values_case1 %>%
  rename(column=c) %>%
  left_join(column_names) %>%
  ggplot(aes(x = fi, y = evsi), color = "black") +
  geom_line()+
  geom_hline(yintercept = c(0.0), color = "darkred",linetype = "dotted")+
  facet_wrap(.~Column_Phase)+
  labs(x="\u03C6", y="EVSI") 
p1
```
## Case 2. Cis-stilbene and Pyrene and Eclipse XDB-CN Phase
### Perfect
```{r dataset-perfect-case2}
datastruct_sim = datastruct;
 idx = c(80,82)
temp_data = dataall%>%filter(ID%in% idx)
temp_data$i = match(temp_data$ID, unique(temp_data$ID))
pKa = analytes_df %>% filter(ID %in% idx) %>% pull(pKa..base.d) %>% replace(is.na(.), -3) %>% replace(. == 100, 10)
pHmpKa = 3.2 - pKa
logP = descriptor_df%>% filter(ID%in% idx) %>% pull(LogP)

nAnalytes_sim = length(unique(temp_data$ID))
nObs_sim = length(temp_data$ID)
datastruct_sim$nAnalytes_sim=nAnalytes_sim;
datastruct_sim$nObs_sim= nObs_sim;
datastruct_sim$logkobs_sim= temp_data$logk;
datastruct_sim$fi_sim = temp_data$fi;
datastruct_sim$logP_sim= logP;
datastruct_sim$pHmpKa_sim= pHmpKa;
datastruct_sim$analyte_sim= match(temp_data$ID, unique(temp_data$ID));
datastruct_sim$column_sim= match(temp_data$column, unique(data$column));

init_sim <- function(){
  list( etaStd  = t(matrix(rep(0,nAnalytes_sim*3), nrow=nAnalytes_sim)),
        dzeta1  = matrix(rep(0,nColumns*nAnalytes_sim), nrow=nAnalytes_sim),
        dzeta2  = matrix(rep(0,nColumns*nAnalytes_sim), nrow=nAnalytes_sim),
        dzeta3  = matrix(rep(0,nColumns*nAnalytes_sim), nrow=nAnalytes_sim))
}
```

```{r run-perfect-case2, eval=F}
fit_opt_perfect <- mod107sim$optimize(
  data = datastruct_sim,
  output_dir = modsim_output_dir,
  output_basename =  paste0(modelsim_name, "-opt-perfect-case2"),
  init =  init_sim,
  jacobian=TRUE)

fit_lap_perfect <- mod107sim$laplace(
  data = datastruct_sim,
  mode = fit_opt_perfect,
  output_dir = modsim_output_dir,
  output_basename = paste0(modelsim_name, "-lap-perfect-case2"))

fit_sam_perfect <- mod107sim$sample(
   data = datastruct_sim,
   output_dir = modsim_output_dir,
   output_basename =  paste0(modelsim_name, "-sam-perfect-case2"),
   init = init_sim,
   iter_warmup = 500,
   iter_sampling = 500,
   chains = 4,
   parallel_chains = 4,
   refresh = 100,
   adapt_delta=0.95
 )
```

```{r read-perfect-case2}
fit_sam_perfect <- cmdstanr::as_cmdstan_fit(c(
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-perfect-case2"), "-1.csv"),
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-perfect-case2"), "-2.csv"),
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-perfect-case2"), "-3.csv"),
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-perfect-case2"), "-4.csv")))
draw_sam_perfect <-fit_sam_perfect$draws("param") 

fit_lap_perfect <- cmdstanr::as_cmdstan_fit(c(paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-lap-perfect-case2"), "-1.csv")))
draw_lap_perfect <-fit_lap_perfect$draws("param") 

plotting_i(draw_sam_perfect)
#plotting_i(draw_lap_perfect)
```

### Single column data
```{r data-scolumn-case2}
datastruct_sim_case2 = datastruct;
 idx = c(80,82)
temp_data = dataall%>%filter(column==2, ID%in% idx)
temp_data$i = match(temp_data$ID, unique(temp_data$ID))
temp_data_all = dataall%>%filter(ID%in% idx)
temp_data_all$i = match(temp_data_all$ID, unique(temp_data_all$ID))
pKa = analytes_df %>%
  filter(ID %in% idx) %>%
  pull(pKa..base.d) %>%
  replace(is.na(.), -3) %>%
  replace(. == 100, 10)
pHmpKa <- 3.2 - pKa
logP = descriptor_df%>% filter(ID%in% idx) %>% pull(LogP)
nAnalytes_sim = length(unique(temp_data$ID))
nObs_sim = length(temp_data$ID)
datastruct_sim_case2$nAnalytes_sim=nAnalytes_sim;
datastruct_sim_case2$nObs_sim= nObs_sim;
datastruct_sim_case2$logkobs_sim= temp_data$logk;
datastruct_sim_case2$fi_sim = temp_data$fi;
datastruct_sim_case2$logP_sim= logP;
datastruct_sim_case2$pHmpKa_sim= pHmpKa;
datastruct_sim_case2$analyte_sim= match(temp_data$ID, unique(temp_data$ID));
datastruct_sim_case2$column_sim= match(temp_data$column, unique(data$column));
```

```{r run-scolumn-case2, eval=F}
fit_opt_scolumn <- mod107sim$optimize(
  data = datastruct_sim_case2,
  output_dir = modsim_output_dir,
  output_basename =  paste0(modelsim_name, "-opt-scolumn-case2"),
  init =  init_sim,
  jacobian=TRUE)

fit_lap_scolumn <- mod107sim$laplace(
  data = datastruct_sim_case2,
  mode = fit_opt_scolumn,
  output_dir = modsim_output_dir,
  output_basename = paste0(modelsim_name, "-lap-scolumn-case2"))

fit_sam_scolumn <- mod107sim$sample(
   data = datastruct_sim_case2,
   output_dir = modsim_output_dir,
   output_basename =  paste0(modelsim_name, "-sam-scolumn-case2"),
   init = init_sim,
   iter_warmup = 500,
   iter_sampling = 500,
   chains = 4,
   parallel_chains = 4,
   refresh = 100,
   adapt_delta=0.95
 )
```

```{r read-scolumn-case2}
fit_sam_scolumn <- cmdstanr::as_cmdstan_fit(c(
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-scolumn-case2"), "-1.csv"),
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-scolumn-case2"), "-2.csv"),
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-scolumn-case2"), "-3.csv"),
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-scolumn-case2"), "-4.csv")))
draw_sam_scolumn <-fit_sam_scolumn$draws("param") 

fit_lap_scolumn <- cmdstanr::as_cmdstan_fit(c(paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-lap-scolumn-case2"), "-1.csv")))
draw_lap_scolumn <-fit_lap_scolumn$draws("param") 

plotting_i(draw_sam_scolumn)
#plotting_i(draw_lap_scolumn)
```

### Simulate future observations
```{r simulate-kobs-case2}
datastruct_sim_gq_case2=datastruct_sim_case2
datastruct_sim_gq_case2$fi_sim_new = rep(seq(0,1,0.05),13);
datastruct_sim_gq_case2$column_sim_new = rep(seq(1,13,1),21);
datastruct_sim_gq_case2$K=length(datastruct_sim_gq_case2$fi_sim_new);

mod107simgq <- cmdstan_model(here(modsimgq_model_dir, modelsimgq_name_ext))

fit107simgq  <- mod107simgq$generate_quantities(fit_sam_scolumn,
                                          data = datastruct_sim_gq_case2,
                                          seed = 123,
                                          parallel_chains = 4,
                                          output_dir = modsimgq_output_dir,
                                          output_basename = paste0(modelsimgq_name, "-sam-scolumn-case2"))

set.seed(2026)
logkobs_future_case2 = fit107simgq$draws(c("n_logkobs","n_fi","n_column")) %>% 
  as_draws_df()%>%
  slice_sample(n=192)  %>%
  tidybayes::spread_draws(n_logkobs[n_exp,n_analyte],n_fi[n_exp],n_column[n_exp]) %>%
  mutate(draw = match(.draw, unique(.draw))) %>%
   select(-c(.iteration, .chain, .draw))
  

logkobs_future_case2%>%
 rename(column=n_column) %>%
  left_join(column_names)%>%
  ggplot(aes(x = n_fi, y = n_logkobs, color = as.factor(n_analyte),fill = as.factor(n_analyte))) +
  ggdist::stat_lineribbon(.width = c(.90), alpha = 1/2) +
  labs(x="\u03C6", y="logk") +
  facet_wrap(.~Column_Phase)+
  coord_cartesian(ylim=c(log10(2),log10(10)))

```

### Current expected utility
```{r current-expected-utility-case2}
current_EU_sam_case2 <- expected_utility(draw_sam_scolumn, seq(0,1,0.05)) %>% mutate(type = "current")
#current_EU_lap_case2 <- expected_utility(draw_lap_scolumn, seq(0,1,0.05)) %>% mutate(type = "current (laplace)")
perfect_EU_sam_case2 <- expected_utility(draw_sam_perfect, seq(0,1,0.05)) %>% mutate(type = "perfect")
#perfect_EU_lap_case2 <- expected_utility(draw_lap_perfect, seq(0,1,0.05)) %>% mutate(type = "perfect (laplace)")

current_best_case2 = max(current_EU_sam_case2$prob)
selected_exp_case2 = current_EU_sam_case2 %>% mutate(n_exp=1:n())%>% filter(prob>=0)

#save for trytonp
x_candidates_case2<-selected_exp_case2$n_exp
saveRDS(
  list(
    datastruct_sim = datastruct_sim_case2,
    logkobs_future = logkobs_future_case2,
    current_best = current_best_case2,
    x_candidates = x_candidates_case2,
    case_names = "case2"
  ),
  file = here::here(modsimdm_model_dir, "input_data.rds")
)

p1 <- rbind(current_EU_sam_case2,perfect_EU_sam_case2) %>%
  rename(column=c) %>%
  left_join(column_names) %>%
  ggplot(aes(x = fi, y = prob, color = type)) +
  geom_line()+
  geom_hline(yintercept = c(0.5), color = "darkred",linetype = "dotted")+
  facet_wrap(.~Column_Phase)+
  labs(x="\u03C6", y="E(Utylity)", color = "Phase") +
  coord_cartesian(ylim=c(0, 1)) 

p1
```

### The expected value of sample information (EVSI) 

```{r, evsi-parallel-case2, eval = FALSE}
x_candidates<-selected_exp_case2$n_exp
evsi_values_case2 <- sapply(x_candidates, \(x) compute_evsi_parralel(x, 
                                                                     .stanmodel= mod107sim,
                                                                     .datastruct_sim =datastruct_sim_case2, 
                                                                     .logkobs_sim = logkobs_future_case2, 
                                                                     .current_best = current_best_case2,
                                                                     .n_future = 20))
  
best_case2 <- x_candidates[which.max(evsi_values_case2)]
selected_exp_case2$evsi = evsi_values_case2$evsi

p1 <- selected_exp_case2 %>%
  rename(column=c) %>%
  left_join(column_names) %>%
  ggplot(aes(x = fi, y = evsi), color = "black") +
  geom_line()+
  geom_hline(yintercept = c(0.0), color = "darkred",linetype = "dotted")+
  facet_wrap(.~Column_Phase)+
  labs(x="\u03C6", y="EVSI") 
p1
```

```{r evsi-parallel-tryton-case2, eval = FALSE}
files <- list.files(
  here(modsimdm_output_dir,"case2"),
  pattern = "^evsi_.*\\.rds$",
  full.names = TRUE
)

# read all files into dataframe
evsi_df <- map_dfr(files, \(f) {
  evsi <- readRDS(f)
  task_id <- str_extract(basename(f), "\\d+") |>as.integer()
  tibble(task_id = task_id,evsi = evsi)
})

evsi_df <- tibble(evsi=evsi_df$evsi,
                  n_exp=evsi_df$task_id,
                  fi = datastruct_sim_gq_case2$fi_sim_new,
                  c = datastruct_sim_gq_case2$column_sim_new) %>% 
  left_join(selected_exp_case2) %>%
  select("n_exp", "c", "fi","prob", "evsi", "type")

write.csv(evsi_df, here(modsimdm_model_dir, "evsi-values-sample-case2.csv"))
```

```{r evsi-plot-case2}
evsi_values_case2<-read.csv(here(modsimdm_model_dir, "evsi-values-sample-case2.csv"))

p1 <- evsi_values_case2 %>%
  rename(column=c) %>%
  left_join(column_names) %>%
  ggplot(aes(x = fi, y = evsi), color = "black") +
  geom_line()+
  geom_hline(yintercept = c(0.0), color = "darkred",linetype = "dotted")+
  facet_wrap(.~Column_Phase)+
  labs(x="\u03C6", y="EVSI")
p1
```

## Case 3. Basic analytes with pKa of 4.9, logP=2, and logkobs of 0.65 at fi =0.40
```{r estimate-case3}
 datastruct_sim_case3 = datastruct;
 nAnalytes_sim = 2
 datastruct_sim_case3$nAnalytes_sim=nAnalytes_sim;
 datastruct_sim_case3$nObs_sim= nAnalytes_sim*nColumns;
 datastruct_sim_case3$logkobs_sim= rep(0.650515,nAnalytes_sim*nColumns);
 datastruct_sim_case3$fi_sim = rep(0.40,nAnalytes_sim*nColumns);
 datastruct_sim_case3$logP_sim= rep(2,nAnalytes_sim);
 datastruct_sim_case3$pHmpKa_sim= c(3.2-4.9,3.2-4.9); #basic;
 datastruct_sim_case3$analyte_sim= rep(seq(1:nAnalytes_sim),nColumns);
 datastruct_sim_case3$column_sim= rep(seq(1:nColumns),nAnalytes_sim);

init_sim <- function(){
  list( etaStd  = t(matrix(rep(0,nAnalytes_sim*3), nrow=nAnalytes_sim)),
        dzeta1  = matrix(rep(0,nColumns*nAnalytes_sim), nrow=nAnalytes_sim),
        dzeta2  = matrix(rep(0,nColumns*nAnalytes_sim), nrow=nAnalytes_sim),
        dzeta3  = matrix(rep(0,nColumns*nAnalytes_sim), nrow=nAnalytes_sim))
}
```

```{r run-scolumn-case3, eval=F}
fit_opt_scolumn <- mod107sim$optimize(
  data = datastruct_sim_case3,
  output_dir = modsim_output_dir,
  output_basename =  paste0(modelsim_name, "-opt-scolumn-case3"),
  init =  init_sim,
  jacobian=TRUE)

fit_lap_scolumn <- mod107sim$laplace(
  data = datastruct_sim_case3,
  mode = fit_opt_scolumn,
  output_dir = modsim_output_dir,
  output_basename = paste0(modelsim_name, "-lap-scolumn-case3"))

fit_sam_scolumn <- mod107sim$sample(
   data = datastruct_sim_case3,
   output_dir = modsim_output_dir,
   output_basename =  paste0(modelsim_name, "-sam-scolumn-case3"),
   init = init_sim,
   iter_warmup = 500,
   iter_sampling = 500,
   chains = 4,
   parallel_chains = 4,
   refresh = 100,
   adapt_delta=0.95
 )
```

```{r read-scolumn-case3}
fit_sam_scolumn <- cmdstanr::as_cmdstan_fit(c(
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-scolumn-case3"), "-1.csv"),
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-scolumn-case3"), "-2.csv"),
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-scolumn-case3"), "-3.csv"),
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-scolumn-case3"), "-4.csv")))
draw_sam_scolumn <-fit_sam_scolumn$draws("param") 

fit_lap_scolumn <- cmdstanr::as_cmdstan_fit(c(paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-lap-scolumn-case3"), "-1.csv")))
draw_lap_scolumn <-fit_lap_scolumn$draws("param") 

plotting_i(draw_sam_scolumn)
#plotting_i(draw_lap_scolumn)
```

### Simulate
```{r simulate-possible-observations-case3}
datastruct_sim_gq_case3=datastruct_sim_case3
datastruct_sim_gq_case3$fi_sim_new = rep(seq(0,1,0.05),13);
datastruct_sim_gq_case3$column_sim_new = rep(seq(1,13,1),21);
datastruct_sim_gq_case3$K=length(datastruct_sim_gq_case3$fi_sim_new);

mod107simgq <- cmdstan_model(here(modsimgq_model_dir, modelsimgq_name_ext))

fit107simgq  <- mod107simgq$generate_quantities(fit_sam_scolumn,
                                          data = datastruct_sim_gq_case3,
                                          seed = 123,
                                          parallel_chains = 4,
                                          output_dir = modsimgq_output_dir,
                                          output_basename = paste0(modelsimgq_name, "-sam-scolumn-case3"))

set.seed(2026)
logkobs_future_case3 = fit107simgq$draws(c("n_logkobs","n_fi","n_column")) %>% 
  as_draws_df()%>%
  slice_sample(n=192)  %>%
  tidybayes::spread_draws(n_logkobs[n_exp,n_analyte],n_fi[n_exp],n_column[n_exp]) %>%
  mutate(draw = match(.draw, unique(.draw))) %>%
   select(-c(.iteration, .chain, .draw))

logkobs_future_case3%>%
 rename(column=n_column) %>%
  left_join(column_names)%>%
  ggplot(aes(x = n_fi, y = n_logkobs, color = as.factor(n_analyte),fill = as.factor(n_analyte))) +
  ggdist::stat_lineribbon(.width = c(.90), alpha = 1/2) +
  labs(x="\u03C6", y="logk") +
  facet_wrap(.~Column_Phase)+
  coord_cartesian(ylim=c(log10(2),log10(10)))
```
### Current expected utility
```{r current-expected-utility-case3}
current_EU_sam_case3 <- expected_utility(draw_sam_scolumn, seq(0,1,0.05)) %>% mutate(type = "current")
#current_EU_lap_case3 <- expected_utility(draw_lap_scolumn, seq(0,1,0.05)) %>% mutate(type = "current (laplace)")

current_best_case3 = max(current_EU_sam_case3$prob)
selected_exp_case3 = current_EU_sam_case3 %>% mutate(n_exp=1:n())%>% filter(prob>=0)

#save for trytonp
x_candidates_case3<-selected_exp_case3$n_exp
saveRDS(
  list(
    datastruct_sim = datastruct_sim_case3,
    logkobs_future = logkobs_future_case3,
    current_best = current_best_case3,
    x_candidates = x_candidates_case3,
    case_names = "case3"
  ),
  file = here::here(modsimdm_model_dir, "input_data.rds")
)

p1 <- rbind(current_EU_sam_case3) %>%
  rename(column=c) %>%
  left_join(column_names) %>%
  ggplot(aes(x = fi, y = evsi), color = "black") +
  geom_line()+
  geom_hline(yintercept = c(0.0), color = "darkred",linetype = "dotted")+
  facet_wrap(.~Column_Phase)+
  labs(x="\u03C6", y="EVSI")

p1
```

### The expected value of sample information (EVSI) 
```{r, evsi-parallel-case3, eval = FALSE}
x_candidates<-selected_exp_case3$n_exp
evsi_values_case3 <- sapply(x_candidates, \(x) compute_evsi_parralel(x, 
                                                                     .stanmodel= mod107sim,
                                                                     .datastruct_sim =datastruct_sim_case3, 
                                                                     .logkobs_sim = logkobs_future_case3, 
                                                                     .current_best = current_best_case3,
                                                                     .n_future = 20))
  
best_case3 <- x_candidates[which.max(evsi_values_case3)]
selected_exp_case3$evsi = evsi_values_case3$evsi

p1 <- selected_exp_case3 %>%
  rename(column=c) %>%
  left_join(column_names) %>%
  ggplot(aes(x = fi, y = evsi), color = "black") +
  geom_line()+
  geom_hline(yintercept = c(0.0), color = "darkred",linetype = "dotted")+
  facet_wrap(.~Column_Phase)+
  labs(x="\u03C6", y="EVSI") 
p1
```

```{r evsi-parallel-tryton-case3, eval = FALSE}
files <- list.files(
  here(modsimdm_output_dir,"case3"),
  pattern = "^evsi_.*\\.rds$",
  full.names = TRUE
)

# read all files into dataframe
evsi_df <- map_dfr(files, \(f) {
  evsi <- readRDS(f)
  task_id <- str_extract(basename(f), "\\d+") |>as.integer()
  tibble(task_id = task_id,evsi = evsi)
})


evsi_df <- tibble(evsi=evsi_df$evsi,
                  n_exp=evsi_df$task_id,
                  fi = datastruct_sim_gq_case3$fi_sim_new,
                  c = datastruct_sim_gq_case3$column_sim_new) %>% 
  left_join(selected_exp_case3) %>%
  select("n_exp", "c", "fi","prob", "evsi", "type")

write.csv(evsi_df, here(modsimdm_model_dir, "evsi-values-sample-case3.csv"))
```

```{r evsi-plot-case3}
evsi_values_case3<-read.csv(here(modsimdm_model_dir, "evsi-values-sample-case3.csv"))

p1 <- evsi_values_case3 %>%
  rename(column=c) %>%
  left_join(column_names) %>%
  ggplot(aes(x = fi, y = evsi), color = "black") +
  geom_line()+
  geom_hline(yintercept = c(0.0), color = "darkred",linetype = "dotted")+
  facet_wrap(.~Column_Phase)+
  labs(x="\u03C6", y="EVSI") 
p1
```

## Case 4. Nautral analytes with logP=2, and logkobs of 0.65 at fi =0.40
```{r dataset-case4}
datastruct_sim_case4 = datastruct;
 nAnalytes_sim = 2
 datastruct_sim_case4$nAnalytes_sim=nAnalytes_sim;
 datastruct_sim_case4$nObs_sim= nAnalytes_sim*nColumns;
 datastruct_sim_case4$logkobs_sim= rep(0.650515,nAnalytes_sim*nColumns);
 datastruct_sim_case4$fi_sim = rep(0.40,nAnalytes_sim*nColumns);
 datastruct_sim_case4$logP_sim= c(2,2);
 datastruct_sim_case4$pHmpKa_sim= c(10,10); #neutral;
 datastruct_sim_case4$analyte_sim= rep(seq(1:nAnalytes_sim),nColumns);
 datastruct_sim_case4$column_sim= rep(seq(1:nColumns),nAnalytes_sim);

init_sim <- function(){
  list( etaStd  = t(matrix(rep(0,nAnalytes_sim*3), nrow=nAnalytes_sim)),
        dzeta1  = matrix(rep(0,nColumns*nAnalytes_sim), nrow=nAnalytes_sim),
        dzeta2  = matrix(rep(0,nColumns*nAnalytes_sim), nrow=nAnalytes_sim),
        dzeta3  = matrix(rep(0,nColumns*nAnalytes_sim), nrow=nAnalytes_sim))
}
```

```{r run-scolumn-case4, eval=F}
fit_opt_scolumn <- mod107sim$optimize(
  data = datastruct_sim_case4,
  output_dir = modsim_output_dir,
  output_basename =  paste0(modelsim_name, "-opt-scolumn-case4"),
  init =  init_sim,
  jacobian=TRUE)

fit_lap_scolumn <- mod107sim$laplace(
  data = datastruct_sim_case4,
  mode = fit_opt_scolumn,
  output_dir = modsim_output_dir,
  output_basename = paste0(modelsim_name, "-lap-scolumn-case4"))

fit_sam_scolumn <- mod107sim$sample(
   data = datastruct_sim_case4,
   output_dir = modsim_output_dir,
   output_basename =  paste0(modelsim_name, "-sam-scolumn-case4"),
   init = init_sim,
   iter_warmup = 500,
   iter_sampling = 500,
   chains = 4,
   parallel_chains = 4,
   refresh = 100,
   adapt_delta=0.95
 )
```

```{r read-scolumn-case4}
fit_sam_scolumn <- cmdstanr::as_cmdstan_fit(c(
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-scolumn-case4"), "-1.csv"),
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-scolumn-case4"), "-2.csv"),
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-scolumn-case4"), "-3.csv"),
                                  paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-sam-scolumn-case4"), "-4.csv")))
draw_sam_scolumn <-fit_sam_scolumn$draws("param") 

fit_lap_scolumn <- cmdstanr::as_cmdstan_fit(c(paste0(modsim_output_dir, "/",  paste0(modelsim_name, "-lap-scolumn-case4"), "-1.csv")))
draw_lap_scolumn <-fit_lap_scolumn$draws("param") 

plotting_i(draw_sam_scolumn)
#plotting_i(draw_lap_scolumn)
```

## Simulate
```{r simulate-possible-observations-case4}
datastruct_sim_gq_case4=datastruct_sim_case4
datastruct_sim_gq_case4$fi_sim_new = rep(seq(0,1,0.05),13);
datastruct_sim_gq_case4$column_sim_new = rep(seq(1,13,1),21);
datastruct_sim_gq_case4$K=length(datastruct_sim_gq_case4$fi_sim_new);

mod107simgq <- cmdstan_model(here(modsimgq_model_dir, modelsimgq_name_ext))

fit107simgq  <- mod107simgq$generate_quantities(fit_sam_scolumn,
                                          data = datastruct_sim_gq_case4,
                                          seed = 123,
                                          parallel_chains = 4,
                                          output_dir = modsimgq_output_dir,
                                          output_basename = paste0(modelsimgq_name, "-sam-scolumn-case1"))

set.seed(2026)
logkobs_future_case4 = fit107simgq$draws(c("n_logkobs","n_fi","n_column")) %>% 
  as_draws_df()%>%
  slice_sample(n=192)  %>%
  tidybayes::spread_draws(n_logkobs[n_exp,n_analyte],n_fi[n_exp],n_column[n_exp]) %>%
  mutate(draw = match(.draw, unique(.draw))) %>%
   select(-c(.iteration, .chain, .draw))

logkobs_future_case4%>%
 rename(column=n_column) %>%
  left_join(column_names)%>%
  ggplot(aes(x = n_fi, y = n_logkobs, color = as.factor(n_analyte),fill = as.factor(n_analyte))) +
  ggdist::stat_lineribbon(.width = c(.90), alpha = 1/2) +
  labs(x="\u03C6", y="logk") +
  facet_wrap(.~Column_Phase)+
  coord_cartesian(ylim=c(log10(2),log10(10)))
```

## Current expected utility
```{r current-expected-utility-case4}
current_EU_sam_case4 <- expected_utility(draw_sam_scolumn, seq(0,1,0.05)) %>% mutate(type = "current")
#current_EU_lap_case4 <- expected_utility(draw_lap_scolumn, seq(0,1,0.05)) %>% mutate(type = "current (laplace)")

current_best_case4 = max(current_EU_sam_case4$prob)
selected_exp_case4 = current_EU_sam_case4 %>% mutate(n_exp=1:n())%>% filter(prob>=0)

#save for trytonp
x_candidates_case4<-selected_exp_case4$n_exp
saveRDS(
  list(
    datastruct_sim = datastruct_sim_case4,
    logkobs_future = logkobs_future_case4,
    current_best = current_best_case4,
    x_candidates = x_candidates_case4,
    case_names = "case4"
  ),
  file = here::here(modsimdm_model_dir, "input_data.rds")
)

p1 <- rbind(current_EU_sam_case4) %>%
  rename(column=c) %>%
  left_join(column_names) %>%
  ggplot(aes(x = fi, y = prob, color = type)) +
  geom_line()+
  geom_hline(yintercept = c(0.5), color = "darkred",linetype = "dotted")+
  facet_wrap(.~Column_Phase)+
  labs(x="\u03C6", y="E(Utylity)", color = "Phase") +
  coord_cartesian(ylim=c(0, 1)) 

p1
```

### The expected value of sample information (EVSI) 
```{r, evsi-parallel-case4, eval = FALSE}
x_candidates<-selected_exp_case4$n_exp
evsi_values_case4 <- sapply(x_candidates, \(x) compute_evsi_parralel(x, 
                                                                     .stanmodel= mod107sim,
                                                                     .datastruct_sim =datastruct_sim_case4, 
                                                                     .logkobs_sim = logkobs_future_case4, 
                                                                     .current_best = current_best_case4,
                                                                     .n_future = 20))
  
best_case4 <- x_candidates[which.max(evsi_values_case4)]
selected_exp_case4$evsi = evsi_values_case4$evsi

p1 <- selected_exp_case4 %>%
  rename(column=c) %>%
  left_join(column_names) %>%
  ggplot(aes(x = fi, y = evsi), color = "black") +
  geom_line()+
  geom_hline(yintercept = c(0.0), color = "darkred",linetype = "dotted")+
  facet_wrap(.~Column_Phase)+
  labs(x="\u03C6", y="EVSI") 
p1
```

```{r evsi-parallel-tryton-case4, eval = FALSE}
files <- list.files(
  here(modsimdm_output_dir,"case4"),
  pattern = "^evsi_.*\\.rds$",
  full.names = TRUE
)

# read all files into dataframe
evsi_df <- map_dfr(files, \(f) {
  evsi <- readRDS(f)
  task_id <- str_extract(basename(f), "\\d+") |>as.integer()
  tibble(task_id = task_id,evsi = evsi)
})

evsi_df <- tibble(evsi=evsi_df$evsi,
                  n_exp=evsi_df$task_id,
                  fi = datastruct_sim_gq_case4$fi_sim_new,
                  c = datastruct_sim_gq_case4$column_sim_new) %>% 
  left_join(selected_exp_case4)  %>%
  select("n_exp", "c", "fi", "evsi")%>%
  mutate(type= "sample")

write.csv(evsi_df, here(modsimdm_model_dir, "evsi-values-sample-case4.csv"))
```

```{r evsi-parallel-tryton-laplace-case4, eval = FALSE}
files <- list.files(
  here(modsimdm_output_dir,"case4"),
  pattern = "^evsi-lap-.*\\.rds$",
  full.names = TRUE
)

# read all files into dataframe
evsi_df <- map_dfr(files, \(f) {
  evsi <- readRDS(f)
  task_id <- str_extract(basename(f), "\\d+") |>as.integer()
  tibble(task_id = task_id,evsi = evsi)
})

evsi_df <- tibble(evsi=evsi_df$evsi,
                  n_exp=evsi_df$task_id,
                  fi = datastruct_sim_gq_case4$fi_sim_new,
                  c = datastruct_sim_gq_case4$column_sim_new) %>% 
  left_join(selected_exp_case4) %>%
  select("n_exp", "c", "fi", "evsi")%>%
  mutate(type= "laplace")

write.csv(evsi_df, here(modsimdm_model_dir, "evsi-values-laplace-case4.csv"))
```

```{r evsi-plot-case4}
evsi_sam_case4<-read.csv(here(modsimdm_model_dir, "evsi-values-sample-case4.csv"))
#evsi_lap_case4<-read.csv(here(modsimdm_model_dir, "evsi-values-laplace-case4.csv"))
p1 <- rbind(evsi_sam_case4) %>%
  rename(column=c) %>%
  left_join(column_names) %>%
  ggplot(aes(x = fi, y = evsi), color = "black") +
  geom_line()+
  geom_hline(yintercept = c(0.0), color = "darkred",linetype = "dotted")+
  facet_wrap(.~Column_Phase)+
  labs(x="\u03C6", y="EVSI")
p1
```

# Session info
```{r}
sessionInfo()
```