---
title: "Model 107. Izocratic Mulitilevel Model with Dewetting, Silanol and pKa effects"
author:
  - name: "Paweł Wiczling*"
    affiliations:
      - name: "Department of Biopharmaceutics and Pharmacodynamics, Medical University of Gdańsk, Gen. J. Hallera 107, 80-416 Gdańsk, Poland"
date: "`r format(Sys.Date())`"
format:
  html:
    theme: cosmo
    toc: true
    code-fold: true  
    code-tools: true
    fig-width: 7
    fig-height: 7
knitr:
  opts_chunk: 
    dev: "ragg_png"
---

# Introductions

In this study, I propose an isocratic multilevel model that accounts for dewetting, silanol interactions, and pKa effects. The model is developed using a dataset available at [link](https://chemrxiv.org/engage/chemrxiv/article-details/64948c82a2c387fa9ac5c1ce), which includes RP-HPLC retention time measurements for 85 analytes (including several duplicates) across 13 columns.

# Setup
```{r setup, message=FALSE}
knitr::opts_chunk$set(cache=FALSE, message=FALSE, error=FALSE, warning=FALSE, comment=NA, out.width='95%')

suppressWarnings(library(dplyr))
suppressWarnings(library(ggplot2))
suppressWarnings(library(patchwork))
suppressWarnings(library(gridExtra))
suppressWarnings(library(naniar))
suppressWarnings(library(knitr))
suppressWarnings(library(data.table))
suppressWarnings(library(tidyverse))
suppressWarnings(library(whisker))
suppressWarnings(library(here))
suppressWarnings(library(cmdstanr))
suppressWarnings(library(posterior))
suppressWarnings(library(bayesplot))
suppressWarnings(library(tidybayes))
suppressWarnings(library(reshape2))
suppressWarnings(library(mrgmisc))
suppressWarnings(library(pracma))
suppressWarnings(library(GGally))
#remotes::install_github("metrumresearchgroup/mrgmisc")
set_cmdstan_path("C:/Users/GUMed/.cmdstan/cmdstan-2.38.0")
select<-dplyr::select
filter<-dplyr::filter
set.seed(10271998) 
source("helper-functions-v100.R")
```

```{r settings}
data_dir = here::here("data")

model_dir <- here::here("model","stan")  
if(!file.exists(model_dir)) dir.create(model_dir, recursive = T)
data_deriv_dir = here::here("data","deriv")
if(!file.exists(data_deriv_dir)) dir.create(data_deriv_dir, recursive = T)
```

```{r set-theme, include = FALSE}
theme_set(theme_bw())
theme_update(
  axis.title = element_text(size = 10, face = "bold"), 
  axis.text = element_text(size = 8), 
  legend.title = element_blank(),
  legend.text = element_text(size = 8),
  legend.key.size = unit(0.4, "cm"),
  strip.text = element_text(size = 8),
  legend.position = "bottom",
  panel.grid.minor = element_blank()
)
```

## Load data
```{r load-data, message=FALSE, warning=FALSE}
dataall <- read.csv(here(data_deriv_dir, "data.csv"), header = TRUE)%>%
  mutate(Compound = HSM3_Name) %>%
  mutate(fi = phi/100,
         logk = log10(k))%>%
  filter(!is.na(logk)) %>%
  group_by(fi, Compound, Column_Phase) %>%
  summarise(logk = mean(logk)) %>%
  ungroup()%>%
   mutate(ID = match(Compound, unique(Compound)),
         column = match(Column_Phase, unique(Column_Phase)))

analytes_names = dataall%>%distinct(ID, .keep_all = T)%>%select(ID, Compound)
column_names = dataall%>%distinct(column, .keep_all = T)%>%select(column,Column_Phase)

smiles <- read.csv(here(data_deriv_dir,"smiles.csv"), sep = ",", header = TRUE)%>%
  select(-ID)%>%
  left_join(analytes_names)%>%arrange(ID)%>%distinct(ID, .keep_all = T)

fg_df = read.csv(file = here(data_deriv_dir,"smarts_functional_groups.csv"), header = TRUE)%>%
  select(-id1,-id2) %>%
  rename(smiles=SMILES) %>%
  left_join(smiles,)%>%arrange(ID)%>%distinct(ID, .keep_all = T)

descriptor_df <- read.csv(file = here(data_deriv_dir,"descriptor_df.csv"), header = TRUE)%>%
  rename(smiles=SMILES) %>%
  left_join(smiles) %>%arrange(ID)%>%distinct(ID, .keep_all = T)

column_df = read.csv(file = here(data_deriv_dir,"columns.csv"), header = TRUE)%>%
  mutate(Column_Phase = str_remove(Phase, "Waters|Agilent"))%>%
  mutate(Column_Phase = str_remove(Column_Phase, " "))%>%
  mutate(Column_Phase = case_when(Column_Phase == "Varian/C18-A" ~ "C18-A",
                                  Column_Phase == "CSH Phenyl- Hexyl"~"CSH Phenyl-Hexyl",
                                 .default = Column_Phase)) %>%
  left_join(column_names) %>%
  rename("carbon_loading" = "Carbon.Loading....",
         "Endcapping" = "Endcapping...."
         ) %>%
  arrange(column)

cation_names = c("Primary_arom_amine",
"Secondary_arom_amine",
"Secondary_aliph_amine",
"Tertiary_aliph_amine",
"Quaternary_aliph_ammonium",
"Secondary_mixed_amine",
"Tertiary_mixed_amine",
"X1.2.Aminoalcohol",
"Hetero_N_basic_H",
"Hetero_N_basic_no_H")

analytes_df = read.csv(file = here(data_deriv_dir,"analytes.csv"), header = TRUE) %>%
   mutate(charge = if_else(pKa..base.d>3.2, 1, 0)) %>%
      mutate(charge =if_else(is.na(charge), 0, charge))
```


## Prepare data
```{r prepare-data, message=FALSE, warning=FALSE}
fg_df <- fg_df %>% mutate(ID = match(ID, unique(ID)))
dataall <- dataall %>% mutate(ID = match(ID, unique(ID)))
analytes_names <- analytes_names %>% mutate(ID = match(ID, unique(ID)))
smiles <-smiles %>% mutate(ID = match(ID, unique(ID)))
descriptor_df <- descriptor_df %>% mutate(ID = match(ID, unique(ID)))
analytes_df  <- analytes_df %>% mutate(ID = match(ID, unique(ID)))

functional_groups = fg_df%>%select(where(~ is.character(.) || !all(. == 0, na.rm = TRUE))) %>%
   select(-smiles, -Anion, -Kation, -Compound )
 functional_groups_names<- colnames(functional_groups)
 totalnrgroups <- summarise_each(functional_groups, funs(sum))
```

## Initial estimates
```{r initial-estimates}
init_aprox <- dataall %>%
  group_by(Compound, ID, column) %>%
  summarise(
    S1 = if_else(n() == 1,-16,polyfit(fi / (1 + 2 * fi), logk, 1)[1]),
    logkw = if_else(n() == 1,polyfit(-16 * fi / (1 + 2 * fi), logk, 0), 
                             polyfit(fi / (1 + 2 * fi), logk, 1)[2]),
    S2 = 2) %>%
  ungroup() %>%
  select(Compound, ID, column, logkw, S2, S1) %>%
  mutate(S1 = -S1 / (1 + 2))

init_vector <- init_aprox %>%
  pivot_longer(cols = c(logkw, S1), names_to = "variable", values_to = "value") %>%
  select(-Compound) %>%
  mutate(variable = case_when(variable=="logkw" ~ "1", 
                              variable=="S1" ~ "2")) %>%
  arrange(variable, column, ID) %>%
  group_by(ID, variable) %>%
  summarize(value = mean(value)) %>%
  group_by(variable) %>%
  mutate(mvalue = mean(value),
         svalue = sd(value)) %>%
  ungroup() %>%
  mutate(value = (value-mvalue)/svalue) %>%
  arrange(variable, ID)
```

# Data analysis

# Stan

Multilevel modeling was performed in [Stan software](https://mc-stan.org/) linked with R/ [cmdstanr](https://mc-stan.org/cmdstanr/). For the inference we used 500 iterations, 1000 warmup iterations, and 8 Markov chains. The reduce_sum function was selected to accelerate the calculations. It works by parallelizing the execution of a single Stan chain across multiple cores. Convergence diagnostics were checked using Gelman−Rubin statistics and trace plots.

## Initialize variables and parameters

```{r stan-setup}
data <- dataall %>% arrange(ID,column,fi)

pKa = analytes_df$pKa..base.d

pKa[is.na(pKa)] = -3
pKa[pKa==100] = 10

pHmpKa = 3.2-pKa

nAnalytes=length(unique(data$ID))
nColumns=length(unique(data$column))
datastruct <- with(data,
                  list(nAnalytes=length(unique(data$ID)),
                       nColumns=length(unique(data$column)),
                       nObs=length(data$ID),
                       analyte=match(data$ID, unique(data$ID)),
                       column=match(data$column, unique(data$column)),
                       fi=data$fi,
                       logP=descriptor_df$LogP,
                       logCL=log10(column_df$carbon_loading),
                       dissociated = analytes_df$charge,
                       pHmpKa = pHmpKa,
                       logkobs=logk,
                       run_estimation=1))


# initialize the values for each variable in each chain:
init <- function(){
  list(   logkw_hat = rnorm(1,2.5,1),
          S1_hat    = rnorm(1,4,1),
          logS2_hat = rnorm(1,log10(2),0.125),
          gamma_hat = rnorm(1,1,0.2),
          alpha_hat = rnorm(1,3,0.2),
          dlogkw_hat=  rnorm(1,-1, 0.1),
          dS1_hat =  rnorm(1,0, 0.5),
          dlogS2_hat =  rnorm(1,0, 0.1),
          fid_hat = 0,
          beta_a_hat  = rnorm(2,c(0.7,0.5),c(0.125,0.1)),
          beta_c_hat  = rnorm(3,0.5,0.2),
          omega_a = c(0.5, 0.5, 0.05)*exp(rnorm(3, 0, 0.1)),
          omega_c = c(0.5, 0.5, 0.5,0.1,0.1,0.1,0.1,0.1)*exp(rnorm(8, 0, 0.1)),
          logomega_dStd = t(matrix(rep(0,nColumns*3), nrow=nColumns)),
          m_logomega_d = c(-0.7, -0.7, -0.7)*exp(rnorm(3, 0, 0.5)),
          sd_logomega_d = c(0.5, 0.5, 0.05)*exp(rnorm(3, 0, 0.1)),
          L_a = t(chol(matrix(c(1,0.75,0.00,0.00,1,0.75,0.00,0.00,1), nrow=3))),
          L_c = t(chol(matrix(c(1,0.75,0.75,0.75,1,0.75,0.75,0.75,1), nrow=3))),
          L_d = diag(3),
          etaStd   = t(matrix(c(init_vector$value,rep(0,nAnalytes)), nrow=nAnalytes)),
          kappaStd = t(matrix(rep(0,nColumns*8), nrow=nColumns)),
          dzeta1  = matrix(rep(0,nColumns*nAnalytes), nrow=nAnalytes),
          dzeta2  = matrix(rep(0,nColumns*nAnalytes), nrow=nAnalytes),
          dzeta3  = matrix(rep(0,nColumns*nAnalytes), nrow=nAnalytes),
          sigma =  0.05*exp(rnorm(1, 0, 0.05))
  )
}
```

## Fitting the model

```{r mod-settings}
model_name <- "mod107"
model_name_ext <- paste0(model_name,".stan")

#' folder shortcuts:
mod_model_dir   <- here::here("model", "stan", model_name)
mod_output_dir   <- here::here("model", "stan", model_name, "output")

if (!file.exists(mod_model_dir)) dir.create(mod_model_dir)
if (!file.exists(mod_output_dir)) dir.create(mod_output_dir)

modelqg_name <- paste0(model_name,"gq")
modelqg_name_ext <- paste0(modelqg_name,".stan")
modgq_model_dir   <- here::here("model", "stan", modelqg_name)
modgq_output_dir   <- here::here("model", "stan", modelqg_name, "output")

if (!file.exists(modgq_model_dir)) dir.create(modgq_model_dir)
if (!file.exists(modgq_output_dir)) dir.create(modgq_output_dir)

modelsim_name <- paste0(model_name,"sim")
modelsim_name_ext <- paste0(modelsim_name,".stan")
modsim_model_dir   <- here::here("model", "stan", modelsim_name)
modsim_output_dir   <- here::here("model", "stan", modelsim_name, "output")

if (!file.exists(modsim_model_dir)) dir.create(modsim_model_dir)
if (!file.exists(modsim_output_dir)) dir.create(modsim_output_dir)
```

```{r stan-compile, eval = FALSE}
mod107 <- cmdstan_model(here::here(mod_model_dir, model_name_ext), stanc_options = list("O1"))
```

We used optimization for initial testing:

```{r stan-optimize, eval = FALSE}
set.seed(1234)

fit_opt <- mod107$optimize(
  data = datastruct,
  output_dir = mod_output_dir,
  output_basename = "opt-mod107",
  init =  init,
  iter=10000
)

fit_opt$print(max_rows=100)
```

```{r plots-optimize, eval = FALSE}
fit_opt <- cmdstanr::as_cmdstan_fit(c(
                                  paste0(mod_output_dir,"/",  "opt-", model_name, "-1.csv")
                                ))

data$logkopt<-fit_opt$mle("logkx")

mle_spread <- enframe(fit_opt$mle("param")) %>%
  mutate(
    idx = str_match(name, "param\\[(\\d+),(\\d+),(\\d+)\\]"),
    i = as.integer(idx[, 2]),
    c = as.integer(idx[, 3]),
     k = as.integer(idx[, 4]),
     param_k = paste0("param.", k),
  ) %>%
  select(i, c, param_k, param = value) %>%
  pivot_wider(
    names_from = param_k,
    values_from = param
  ) %>%
  rename(ID=i) %>%
  left_join(analytes_names) %>%
  rename(column=c) %>%
  left_join(column_names) 

plotting_i = function(idx, temp_data, data) {
temp_data%>%
  filter(ID %in% idx) %>%
  tidyr::expand_grid(fi = seq(0,1,0.01)) %>%
  mutate(logk =  funlogki_pKa_v102(param.1,param.2,param.3,param.4,param.5,param.6,param.7,param.8,param.9,param.10, fi)) %>%
  ggplot(aes(x = fi, y = logk, color = as.factor(column))) +
  geom_line() + 
  geom_point(data = filter(data,ID %in% idx),aes(x=fi, y=logk, color = as.factor(column))) + 
  facet_wrap(~Column_Phase)+
  labs(title = analytes_names$Compound[idx], x="\u03C6", y="logk (individual)") +
  theme(legend.position = "none") +
  coord_cartesian(xlim=c(0,1),ylim=c(-1,2))
}

init_param_names = c("logkw_hat","S1_hat","logS2_hat", "fid_hat", "alpha_hat", "dlogkw_hat", "dS1_hat", "dlogS2_hat", "gamma_hat","beta_a_hat","beta_c_hat","omega_a","omega_c","logomega_dStd", "m_logomega_d", "sd_logomega_d", "L_a","L_c","L_d","etaStd","kappaStd","dzeta1","dzeta2","dzeta3","sigma")

init_list <- function(){
output = fit_opt$mle(init_param_names)
init0 <- stan_init_from_flat(output)
output <- output*exp(rnorm(length(output), 0, 0.05))
init <- stan_init_from_flat(output)

init$L_a=t(chol(as.matrix(Matrix::nearPD(init0$L_a %*% t(init0$L_a), corr = TRUE)$mat)))
init$L_c=t(chol(as.matrix(Matrix::nearPD(init0$L_c %*% t(init0$L_c), corr = TRUE)$mat)))
init$L_d=t(chol(as.matrix(Matrix::nearPD(init0$L_d %*% t(init0$L_d), corr = TRUE)$mat)))

return(init)
}

#map(c(7,26,40,49,56,57,71), \(x) plotting_i(x, mle_spread, data))
```

```{r stan-optimize-test, eval = FALSE}
set.seed(1234)
fit_opt2 <- mod107$optimize(
  data = datastruct,
  output_dir = mod_output_dir,
  output_basename = "opt2-mod107",
  init =  init_list,
  iter=10000
)

fit_opt2$print(max_rows=100)
```

```{r plots-optimize-test}

fit_opt2 <- cmdstanr::as_cmdstan_fit(c(
                                  paste0(mod_output_dir,"/",  "opt2-", model_name, "-1.csv")
                                ))

data$logkopt<-fit_opt2$mle("logkx")

mle_spread <- enframe(fit_opt2$mle("param")) %>%
  mutate(
    idx = str_match(name, "param\\[(\\d+),(\\d+),(\\d+)\\]"),
    i = as.integer(idx[, 2]),
    c = as.integer(idx[, 3]),
     k = as.integer(idx[, 4]),
     param_k = paste0("param.", k),
  ) %>%
  select(i, c, param_k, param = value) %>%
  pivot_wider(
    names_from = param_k,
    values_from = param
  ) %>%
  rename(ID=i) %>%
  left_join(analytes_names) %>%
  rename(column=c) %>%
  left_join(column_names) 

plotting_i = function(idx, temp_data, data) {
temp_data%>%
  filter(ID %in% idx) %>%
  tidyr::expand_grid(fi = seq(0,1,0.01)) %>%
  mutate(logk =  funlogki_pKa_v102(param.1,param.2,param.3,param.4,param.5,param.6,param.7,param.8,param.9,param.10,fi)) %>%
  ggplot(aes(x = fi, y = logk, color = as.factor(column))) +
  geom_line() + 
  geom_point(data = filter(data,ID %in% idx),aes(x=fi, y=logk, color = as.factor(column))) + 
  facet_wrap(~Column_Phase)+
  labs(title = analytes_names$Compound[idx], x="\u03C6", y="logk (individual)") +
  theme(legend.position = "none") +
  coord_cartesian(xlim=c(0,1),ylim=c(-1,2))
}

init_param_names = c("logkw_hat","S1_hat","logS2_hat", "fid_hat", "alpha_hat", "dlogkw_hat", "dS1_hat", "dlogS2_hat", "gamma_hat","beta_a_hat","beta_c_hat","omega_a","omega_c","logomega_dStd", "m_logomega_d", "sd_logomega_d", "L_a","L_c","L_d","etaStd","kappaStd","dzeta1","dzeta2","dzeta3","sigma")

init_list <- function(){
output = fit_opt$mle(init_param_names)
init0 <- stan_init_from_flat(output)
output <- output*exp(rnorm(length(output), 0, 0.05))
init <- stan_init_from_flat(output)

init$L_a=t(chol(as.matrix(Matrix::nearPD(init0$L_a %*% t(init0$L_a), corr = TRUE)$mat)))
init$L_c=t(chol(as.matrix(Matrix::nearPD(init0$L_c %*% t(init0$L_c), corr = TRUE)$mat)))
init$L_d=t(chol(as.matrix(Matrix::nearPD(init0$L_d %*% t(init0$L_d), corr = TRUE)$mat)))


return(init)
}

p2<-data %>%
  ggplot(aes(x=logkopt, y=logk, color = as.factor(column))) + 
  geom_point() + 
  facet_wrap(~column) +
  labs(x =  expression(logkp), y = expression(logk)) + 
  theme(legend.position="none", 
        axis.text =element_text(size = 8),
        strip.text =element_text(size = 8))

p2
map(c(7,26,40,49,56,57,71), \(x) plotting_i(x, mle_spread, data))
```

For local computations one can use cmdstanr:

```{r stan-sample-ppc, eval = FALSE}
datastruct_ppc = datastruct;
datastruct_ppc$run_estimation=0;
 fitp <- mod107$sample(
   data = datastruct_ppc,
   output_dir = mod_output_dir,
   output_basename = "ppc-mod107",
   init = init,
   iter_warmup = 1000,
   iter_sampling = 500,
   chains = 8,
   parallel_chains = 8,
   refresh = 100,
   adapt_delta=0.9
 )
```

```{r stan-sample, eval = FALSE}
 fit <- mod107$sample(
   data = datastruct,
   output_dir = mod_output_dir,
   output_basename = "loc-mod107",
   init = init,
   iter_warmup = 1000,
   iter_sampling = 500,
   chains = 8,
   parallel_chains = 8,
   refresh = 100,
   adapt_delta=0.9
 )
 # fit$save_object(file = here(mod_output_dir,"loc-mod107.RDS"))
```

We performed out computations at the Academic Computer Center in Gdańsk, [Tryton Cluster](https://docs.task.gda.pl/kdm/zasoby-sprzetowe/tryton/). In this case:

1.  write the necessary data to .json format

```{r dump-files, eval = FALSE}
write_stan_json(datastruct, paste0(mod_model_dir,"/standata.json"), always_decimal = FALSE)
write_stan_json(init_list(), paste0(mod_model_dir,"/init-1.json"), always_decimal = FALSE)
write_stan_json(init_list(), paste0(mod_model_dir,"/init-2.json"), always_decimal = FALSE)
write_stan_json(init_list(), paste0(mod_model_dir,"/init-3.json"), always_decimal = FALSE)
write_stan_json(init_list(), paste0(mod_model_dir,"/init-4.json"), always_decimal = FALSE)
write_stan_json(init_list(), paste0(mod_model_dir,"/init-5.json"), always_decimal = FALSE)
write_stan_json(init_list(), paste0(mod_model_dir,"/init-6.json"), always_decimal = FALSE)
write_stan_json(init_list(), paste0(mod_model_dir,"/init-7.json"), always_decimal = FALSE)
write_stan_json(init_list(), paste0(mod_model_dir,"/init-8.json"), always_decimal = FALSE)
write_stan_json(init_list(), paste0(mod_model_dir,"/init-9.json"), always_decimal = FALSE)
write_stan_json(init_list(), paste0(mod_model_dir,"/init-10.json"), always_decimal = FALSE)
```

2.  run the model using the batch file:

```{=html}
<pre> 
#!/bin/bash -l

#SBATCH --job-name=cmdstan_conda_batch
#SBATCH -N 1
#SBATCH -n 48
#SBATCH -p batch
#SBATCH --time=48:00:00
#SBATCH --mem=24gb
#SBATCH --array=1-10%10 

# load
# personal CmdStan 2.38.0
export CMDSTAN_DIR=$HOME/cmdstan/2.38.0
export PATH=$CMDSTAN_DIR/bin:$PATH

export STAN_THREADS=true

# model name
export CMDSTAN_MODEL_NAME="mod107"

# paths
export MODEL_SRC_DIR="/users/project1/pt01268/mod107/"
cd ${CMDSTAN_DIR}

# build/compile
[ -f ${MODEL_SRC_DIR}/${CMDSTAN_MODEL_NAME} ] && echo "Model " ${CMDSTAN_MODEL_NAME} " exists." || make ${MODEL_SRC_DIR}/${CMDSTAN_MODEL_NAME}

wait

cd ${MODEL_SRC_DIR}

${MODEL_SRC_DIR}/${CMDSTAN_MODEL_NAME} sample num_samples=500 num_warmup=1000 algorithm=hmc engine=nuts max_depth=14 adapt delta=0.95 data file=$MODEL_SRC_DIR/standata.json init=$MODEL_SRC_DIR/init-${SLURM_ARRAY_TASK_ID}.json  num_threads=${SLURM_NTASKS} output file=$MODEL_SRC_DIR/${CMDSTAN_MODEL_NAME}-${SLURM_ARRAY_TASK_ID}.csv
wait
</pre>
```

3.  load the output files using cmdstanr. 

```{r stan-load}
fit <- cmdstanr::as_cmdstan_fit(c(
                                  paste0(mod_output_dir,"/",  model_name, "-1.csv"),
                                  paste0(mod_output_dir,"/",  model_name, "-2.csv"),
                                  paste0(mod_output_dir,"/",  model_name, "-3.csv"),
                                  paste0(mod_output_dir,"/",  model_name, "-4.csv"),
                                  paste0(mod_output_dir,"/",  model_name, "-5.csv"),
                                  paste0(mod_output_dir,"/",  model_name, "-6.csv"),
                                  paste0(mod_output_dir,"/",  model_name, "-7.csv"),
                                  paste0(mod_output_dir,"/",  model_name, "-8.csv")
                                ))
fitp <- cmdstanr::as_cmdstan_fit(c(
                                  paste0(mod_output_dir,"/","ppc-", model_name, "-1.csv"),
                                  paste0(mod_output_dir,"/","ppc-", model_name, "-2.csv"),
                                  paste0(mod_output_dir,"/","ppc-", model_name, "-3.csv"),
                                  paste0(mod_output_dir,"/","ppc-", model_name, "-4.csv"),
                                  paste0(mod_output_dir,"/","ppc-", model_name, "-5.csv"),
                                  paste0(mod_output_dir,"/","ppc-", model_name, "-6.csv"),
                                  paste0(mod_output_dir,"/","ppc-", model_name, "-7.csv"),
                                  paste0(mod_output_dir,"/","ppc-", model_name, "-8.csv")
                                ))
# posterior::subset_draws(fit$draws(), variable = c("sigma"), chain = c(1,2,3,4,5,6,7,8)) %>% mcmc_trace()
# posterior::subset_draws(fit$draws(), variable = c("sigma"), chain = c(1,2,3,4,5,6,7,10))%>%summarise_draws(default_convergence_measures())
```

4.  check the diagnostics of Monte Carlo inferences based on the Stan documentation described herein [diagnose](https://mc-stan.org/docs/cmdstan-guide/diagnose.html)

```{r stan-diagnose, eval = FALSE}
 #fit$cmdstan_diagnose()
 setwd(mod_output_dir)
 str = paste0(cmdstan_path(), '/bin/diagnose  mod107-*.csv')
 system(str,intern=TRUE)
```

The diagnostics are reasonable given model complexity. Output copied here to save time:

```{=html}
<pre>
"Checking sampler transitions treedepth."
"Treedepth satisfactory for all transitions."
"Checking sampler transitions for divergences."
"No divergent transitions found."
"Checking E-BFMI - sampler transitions HMC potential energy."
"E-BFMI satisfactory."                                                      
"Rank-normalized split effective sample size satisfactory for all parameters."
"The following parameters had rank-normalized split R-hat greater than 1.01:" 
"etaStd[1,1], etaStd[1,2], etaStd[1,3], etaStd[1,4], etaStd[1,5], etaStd[1,6], etaStd[1,7], etaStd[1,8], etaStd[1,9], etaStd[1,10], etaStd[1,11], etaStd[1,12], etaStd[1,13], etaStd[3,13], etaStd[1,14], etaStd[1,15], etaStd[1,16], etaStd[1,17], etaStd[1,21], etaStd[1,22], etaStd[1,23], etaStd[1,24], etaStd[1,25], etaStd[1,26], etaStd[1,27], etaStd[1,28], etaStd[1,29], etaStd[1,30], etaStd[3,30], etaStd[1,31], etaStd[1,33], etaStd[1,34], etaStd[1,35], etaStd[1,36], etaStd[2,36], etaStd[1,37], etaStd[1,38], etaStd[1,39], etaStd[1,40], etaStd[2,40], etaStd[1,41], etaStd[3,43], etaStd[3,44], etaStd[1,46], etaStd[3,59], dzeta3[7,1], dzeta3[24,1], dzeta3[25,1], dzeta3[40,1], dzeta3[42,1], dzeta3[86,1]"
"Such high values indicate incomplete mixing and biased estimation."
"You should consider regularizing your model with additional prior information or a more effective parameterization."                                               
"Processing complete." 
</pre>
```

## Summary of model parameters (table):

The [stansummary](https://mc-stan.org/docs/cmdstan-guide/stansummary.html) function was used to report summary and diagnostic statistics over model parameters. 

### Priors
```{r ppc-summary}
param_names = c("logkw_hat","S1_hat","logS2_hat", "fid_hat", "alpha_hat", "dlogkw_hat", "dS1_hat", "dlogS2_hat", "gamma_hat","beta_a_hat","beta_c_hat","omega_a","omega_c", "m_logomega_d", "sd_logomega_d", "rho_a","rho_c","rho_d","sigma")

fitp$print(variables = param_names, max_rows=59)
```
### Posterior
```{r summary}
param_names = c("logkw_hat","S1_hat","logS2_hat", "fid_hat", "alpha_hat", "dlogkw_hat", "dS1_hat", "dlogS2_hat", "gamma_hat","beta_a_hat","beta_c_hat","omega_a","omega_c", "m_logomega_d", "sd_logomega_d", "rho_a","rho_c","rho_d","sigma")

parameter_estimates<-fit$summary(variables = param_names)
parameter_estimates_2<-fit$summary(variables = c("kappa"))
parameter_estimates_3<-fit$summary(variables = c("omega_d1","omega_d2","omega_d3"))

fit$print(variables = param_names, max_rows=59)
```

### Paramters in copy-ready format
```{r summary2, eval = FALSE, echo=FALSE}
param_names = c("logkw_hat","S1_hat","logS2_hat", "fid_hat", "alpha_hat", "dlogkw_hat", "dS1_hat", "dlogS2_hat", "gamma_hat","beta_a_hat","beta_c_hat","omega_a","omega_c", "m_logomega_d", "sd_logomega_d", "L_a","L_c","L_d","sigma")

x<-fit$summary(variables = param_names, "mean", "sd") %>%
  mutate(cv = sd/mean*100)%>% mutate(x = paste0(variable, "=", mean, ";"))
print(x, n=59)
cat(x$x, sep = "\n") 

x<-fit$summary(variables = "kappaStd", "mean", "sd") %>%
  mutate(cv = sd/mean*100)%>% mutate(x = paste0(variable, "=", mean, ";"))
cat(x$x, sep = "\n") 

x<-fit$summary(variables = "logomega_dStd", "mean", "sd") %>%
  mutate(cv = sd/mean*100)%>% mutate(x = paste0(variable, "=", mean, ";"))
cat(x$x, sep = "\n") 
```

## Genereted quantitites
```{r generete-quntities, eval=F}
mod107gq <- cmdstan_model(here(modgq_model_dir,modelqg_name_ext))
fitgq  <- mod107gq$generate_quantities(fit,
                                          data = datastruct,
                                          seed = 123,
                                          parallel_chains = 8,
                                          output_dir = modgq_output_dir,
                                          output_basename = modelqg_name)
fitpgq  <- mod107gq$generate_quantities(fitp,
                                          data = datastruct,
                                          seed = 123,
                                          parallel_chains = 8,
                                          output_dir = modgq_output_dir,
                                          output_basename = paste0("ppc-",modelqg_name))
```

# Results
## Load
```{r eta-load}
fitgq <- cmdstanr::read_cmdstan_csv(c(
                                  paste0(modgq_output_dir, "/",  modelqg_name, "-1.csv"),
                                  paste0(modgq_output_dir, "/",  modelqg_name, "-2.csv"),
                                  paste0(modgq_output_dir, "/",  modelqg_name, "-3.csv"),
                                  paste0(modgq_output_dir, "/",  modelqg_name, "-4.csv"),
                                  paste0(modgq_output_dir, "/",  modelqg_name, "-5.csv"),
                                  paste0(modgq_output_dir, "/",  modelqg_name, "-6.csv"), 
                                  paste0(modgq_output_dir, "/",  modelqg_name, "-7.csv"),
                                  paste0(modgq_output_dir, "/",  modelqg_name, "-8.csv")
                                ))
draws_gen_df <- as_draws_df(fitgq$generated_quantities) %>% tidyr::drop_na()

fitpgq <- cmdstanr::read_cmdstan_csv(c(
                                  paste0(modgq_output_dir, "/","ppc-",  modelqg_name, "-1.csv"),
                                  paste0(modgq_output_dir, "/","ppc-",  modelqg_name, "-2.csv"),
                                  paste0(modgq_output_dir, "/","ppc-",  modelqg_name, "-3.csv"),
                                  paste0(modgq_output_dir, "/","ppc-",  modelqg_name, "-4.csv"),
                                  paste0(modgq_output_dir, "/","ppc-",  modelqg_name, "-5.csv"),
                                  paste0(modgq_output_dir, "/","ppc-",  modelqg_name, "-6.csv"), 
                                  paste0(modgq_output_dir, "/","ppc-",  modelqg_name, "-7.csv"),
                                  paste0(modgq_output_dir, "/","ppc-",  modelqg_name, "-8.csv")
                                ))
drawsp_gen_df <- as_draws_df(fitgq$generated_quantities) %>% tidyr::drop_na()
```


## Trace plots

Trace plots are time series plots of Markov chains. Here we show standard trace plots for several parameters
```{r trace-plots, include=TRUE}
bayesplot::mcmc_trace(fit$draws(c("logkw_hat","S1_hat","logS2_hat","gamma_hat","dlogkw_hat","dS1_hat")))
bayesplot::mcmc_trace(fit$draws(c("omega_a","omega_c","rho_a[2,1]","rho_a[3,1]","rho_a[3,2]", "rho_c[2,1]","rho_c[3,1]","rho_c[3,2]","sigma"))) 
bayesplot::mcmc_trace(fit$draws(c("beta_a_hat","beta_c_hat"))) 
bayesplot::mcmc_trace(fit$draws(c("m_logomega_d","sd_logomega_d","rho_d[2,1]","rho_d[3,1]","rho_d[3,2]")))
bayesplot::mcmc_trace(fit$draws(c("omega_d1"))) 
bayesplot::mcmc_trace(fit$draws(c("omega_d2"))) 
bayesplot::mcmc_trace(fit$draws(c("omega_d3")))

# mcmc_pairs(
#   fit$draws(),
#   pars = c("dlogS2_hat", "kappa[2,8]", "kappa[3,8]"), # Replace with your parameter names
#   off_diag_args = list(size = 1, alpha = 0.5) # Customize plots
# )

```

## Summary of model parameters (figures)

```{r mcmc-intervals-part1}
params_to_plot<-c("logkw_hat","S1_hat","logS2_hat","gamma_hat",
               "alpha_hat","dS1_hat","dlogkw_hat","dlogS2_hat","beta_a_hat", "beta_c_hat")

p1<-plot_prior_post_intervals(fitp,fit,params_to_plot)+
  scale_y_discrete(labels = c("logkw_hat"=expression(theta^{"(" * logkw * ")"}), 
                              "S1_hat"= expression(theta^{"(" * S1 * ")"}),
                              "logS2_hat"=expression(theta^{"(" * logS2 * ")"}),
                              "gamma_hat"= expression(theta^{"(" * gamma * ")"}),
                              "alpha_hat"=expression(theta^{"(" * alpha * ")"}),
                              "dlogkw_hat"=expression(theta^{"(" * dlogkw * ")"}),
                              "dS1_hat"=expression(theta^{"(" * dS1 * ")"}),
                              "dlogS2_hat"=expression(theta^{"(" * dlogS2 * ")"}),
                              "beta_a_hat[1]"=expression(beta*a^{"(" * logkw * ")"}), 
                              "beta_a_hat[2]"= expression(beta*a^{"(" * S1 * ")"}),
                              "beta_c_hat[1]"=expression(beta*c^{"(" * logkw * ")"}), 
                              "beta_c_hat[2]"= expression(beta*c^{"(" * S1 * ")"}), 
                              "beta_c_hat[3]"= expression(beta*c^{"(" * logS2 * ")"})),
                   limits = t(rev(c("logkw_hat",
                               "S1_hat",
                               "logS2_hat",
                               "gamma_hat",
                               "alpha_hat",
                               "dlogkw_hat",
                               "dS1_hat","dlogS2_hat",
                               "beta_a_hat[1]",
                               "beta_a_hat[2]",
                               "beta_c_hat[1]",
                               "beta_c_hat[2]",
                               "beta_c_hat[3]"))))

params_to_plot<-c("omega_a","rho_a[2,1]","rho_a[3,1]","rho_a[3,2]")

p2<-plot_prior_post_intervals(fitp,fit,params_to_plot)+
  scale_y_discrete(labels = c("omega_a[1]"= expression(omega*a^{"(" * logkw * ")"}),
                              "omega_a[2]"= expression(omega*a^{"(" * S1 * ")"}),
                              "omega_a[3]"= expression(omega*a^{"(" * logS2 * ")"}),
                              "rho_a[2,1]"=expression(rho*a^{"(" * logkw*"-"*S1 * ")"}), 
                              "rho_a[3,1]"=expression(rho*a^{"(" * logkw*"-"*logS2 * ")"}), 
                              "rho_a[3,2]"=expression(rho*a^{"(" * S1*"-"*logS2 * ")"})), 
                   limits = t(rev(c("omega_a[1]",
                               "omega_a[2]","omega_a[3]",
                               "rho_a[2,1]","rho_a[3,1]",
                               "rho_a[3,2]"))))

params_to_plot<-c("omega_c","rho_c[2,1]","rho_c[3,1]","rho_c[3,2]")

p3<-plot_prior_post_intervals(fitp,fit,params_to_plot)+
  scale_y_discrete(labels = c("omega_c[1]"= expression(omega*c^{"(" * logkw * ")"}),  
                              "omega_c[2]"= expression(omega*c^{"(" * S1 * ")"}),  
                              "omega_c[3]"= expression(omega*c^{"(" * logS2 * ")"}),  
                              "omega_c[4]"= expression(omega*c^{"(" * gamma * ")"}), 
                              "omega_c[5]"= expression(omega*c^{"(" * fi[d] * ")"}),
                              "rho_c[2,1]"= expression(rho*c^{"(" * logkw*"-"*S1 * ")"}), 
                              "rho_c[3,1]"= expression(rho*c^{"(" * logkw*"-"*logS2 * ")"}), 
                              "rho_c[3,2]"= expression(rho*c^{"(" * S1*"-"*logS2 * ")"})), 
                   limits = t(rev(c("omega_c[1]",
                               "omega_c[2]",
                               "omega_c[3]",
                               "omega_c[4]",
                               "omega_c[5]",
                               "rho_c[2,1]",
                               "rho_c[3,1]",
                               "rho_c[3,2]"))))

 
params_to_plot<-    c("m_logomega_d","sd_logomega_d","rho_d[2,1]","rho_d[3,1]","rho_d[3,2]") 
 
p4<-plot_prior_post_intervals(fitp,fit, params_to_plot, transformations =
                                list("m_logomega_d[1]" = "exp",
                                     "m_logomega_d[2]" = "exp",
                                     "m_logomega_d[3]" = "exp"))+
  scale_y_discrete(labels = c("exp(m_logomega_d[1])"= expression(m*omega*d^{"(" * logkw * ")"}), 
                              "exp(m_logomega_d[2])"= expression(m*omega*d^{"(" * S1 * ")"}),
                              "exp(m_logomega_d[3])"= expression(m*omega*d^{"(" * logS2 * ")"}),
                              "sd_logomega_d[1]"= expression(sd*omega*d^{"(" * logkw * ")"}), 
                              "sd_logomega_d[2]"= expression(sd*omega*d^{"(" * S1 * ")"}),
                              "sd_logomega_d[3]"= expression(sd*omega*d^{"(" * logS2 * ")"}),
                              "rho_d[2,1]"=expression(rho*d^{"(" * logkw*"-"*S1 * ")"}),
                              "rho_d[3,1]"=expression(rho*d^{"(" * logkw*"-"*logS2 * ")"}), 
                              "rho_d[3,2]"=expression(rho*d^{"(" * S1*"-"*logS2 * ")"})), 
                   limits = t(rev(c("exp(m_logomega_d[1])","exp(m_logomega_d[2])","exp(m_logomega_d[3])",
                               "sd_logomega_d[1]","sd_logomega_d[2]","sd_logomega_d[3]",
                               "rho_d[2,1]","rho_d[3,1]",
                               "rho_d[3,2]"))))

parameter_estimates_1_fig <- (p1+p2)/(p3+p4)
parameter_estimates_1_fig
```



```{r mcmc-intervals-part2}
#| fig-width: 6
#| fig-height: 6
draws_df_subset <- fit$draws(format = "df",variable = c("kappa","ctheta","omega_d1","omega_d2","omega_d3","logkw_hat", "S1_hat", "logS2_hat", "gamma_hat", "fid_hat", "dlogkw_hat", "dS1_hat", "dlogS2_hat"))
drawsp_df_subset <- fitp$draws(format = "df",variable = c("kappa","ctheta","omega_d1","omega_d2","omega_d3","logkw_hat", "S1_hat", "logS2_hat", "gamma_hat", "fid_hat", "dlogkw_hat", "dS1_hat", "dlogS2_hat"))

make_intervals_omegad <- function(draws_df, type) {
  draws_df %>%
    slice_sample(n = 1000) %>%
    spread_draws(omega_d1[c], omega_d2[c], omega_d3[c]) %>%
    pivot_longer(
      c(omega_d1, omega_d2, omega_d3),
      names_to = "Parameter",
      values_to = "Value"
    ) %>%
  mutate(Parameter = factor(Parameter,
                     levels = c("omega_d1", "omega_d2", "omega_d3"))) %>%
    mutate(column = c) %>%
    left_join(column_df, by = "column") %>%
    group_by(Parameter, `Stationary Phase` = Column_Phase) %>%
    median_qi(Value, .width=c(0.5,0.9)) %>%
    ungroup() %>%
    mutate(
      type = type,
      Parameter = recode(
        Parameter,
        omega_d1 = 'omega*d[c]^(logkw)',
        omega_d2 = 'omega*d[c]^(S1)',
        omega_d3 = 'omega*d[c]^(logS2)'
      )
    )
}

results_post_1 <- make_intervals_omegad(draws_df_subset, "Posterior") %>%select(-type)
# results_prior_1 <- make_intervals_omegad(drawsp_df_subset, "Prior")%>%select(-type)

parameter_estimates_2_fig <- ggplot() +
  tidybayes::geom_pointinterval(
    data = results_post_1,
    aes(
      y = `Stationary Phase`,
      x = Value,
      xmin = .lower,
      xmax = .upper
    ),
    colour = "#0072B2",
       point_size = 1
  ) +
  facet_wrap(~Parameter, scales = "free_x", labeller = label_parsed) + 
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank())

make_intervals_kappa <- function(draws_df, type) {

df_subset<- draws_df %>%
    slice_sample(n = 1000) 
 
temp_a<-df_subset %>%
    spread_draws(kappa[c,j],logkw_hat, S1_hat, logS2_hat, gamma_hat, 
                 fid_hat, dlogkw_hat, dS1_hat, dlogS2_hat) 
temp_b<-df_subset %>%
    spread_draws(ctheta[c,j])
temp_c<-df_subset %>%
  spread_draws(kappa[c,j])%>%
  rename(kappaN=kappa) %>%
  filter(j%in%c(1,2,3)) %>%
  mutate(j=j+5)

temp_a %>% 
  left_join(temp_b) %>%
  left_join(temp_c) %>%
  mutate(ctheta = coalesce(ctheta, 0)) %>%
  mutate(kappaN = coalesce(kappaN, 0)) %>%
  mutate(kappa = kappa + ctheta+kappaN)%>%
  mutate(kappa = case_when(
    j==1 ~ kappa + logkw_hat,
    j==2 ~ kappa + S1_hat,
    j==3 ~ kappa + logS2_hat,
    j==4 ~ kappa + gamma_hat,
    j==5 ~ kappa + fid_hat,
    j==6 ~ kappa + logkw_hat+dlogkw_hat,
    j==7 ~ kappa + S1_hat+dS1_hat,
    j==8 ~ kappa + logS2_hat+dlogS2_hat,
    TRUE   ~ kappa
    )) %>%
    mutate(column = c) %>%
    left_join(column_df, by = "column") %>%
    group_by(j, `Stationary Phase` = Column_Phase) %>%
    tidybayes::median_qi(`Value`=kappa, .width=c(0.5,0.9)) %>%
  mutate(Parameter = factor(
    recode(j,
    '1' = 'logkw*(neutral)',
    '2' = 'S1*(neutral)',
    '3' = 'logS2*(neutral)',
    '4' = 'gamma*(basic)',
    '5' = 'fid',
    '6' = 'logkw*(basic)',
    '7' = 'S1*(basic)',
    '8' = 'logS2*(basic)'
    ),
    levels = c(
      "logkw*(neutral)",
      "S1*(neutral)",
      "logS2*(neutral)",
      "fid",
      "logkw*(basic)",
      "S1*(basic)",
      "logS2*(basic)", 
      "gamma*(basic)"
    )))
}

results_post_2 <- make_intervals_kappa(draws_df_subset, "Posterior")%>% select(colnames(results_post_1))

parameter_estimates_3_fig <- ggplot() +
  tidybayes::geom_pointinterval(
    data = results_post_2,
    aes(
      y = `Stationary Phase`,
      x = Value,
      xmin = .lower,
      xmax = .upper
    ),
    colour = "#0072B2",
       point_size = 1
  ) +
  facet_wrap(.~Parameter, scales = "free_x", nrow=2,labeller = label_parsed)+
  theme(
    axis.title.x = element_blank(),
    
    axis.text = element_text(size = 6),
    strip.text = element_text(size = 8)
  )

parameter_estimates_fig <- parameter_estimates_3_fig/(parameter_estimates_2_fig +
  plot_layout(widths = c(3,1))) +
  plot_layout(heights = c(2, 1), guides = "collect") &
  theme(axis.title = element_text(size = 10, face = "bold"), 
  axis.text = element_text(size = 8), 
  legend.title = element_blank(),
  legend.text = element_text(size = 8),
  legend.key.size = unit(0.4, "cm"),
  strip.text = element_text(size = 8),
  legend.position = "bottom",
  panel.grid.minor = element_blank())


parameter_estimates_fig
```

## Concordance plots
```{r ind-pop-gof-plots}
results_ind <-draws_gen_df %>%
  slice_sample(n=200) %>%
  tidybayes::spread_draws(slogk_ind[i]) %>% 
  rename(ID=i) %>%
  group_by(ID)%>%
  tidybayes::median_qi(logkpred = slogk_ind) %>%
  select(-ID)

results_pop <-draws_gen_df %>%
  slice_sample(n=200) %>%
  tidybayes::spread_draws(slogk_pop[i]) %>% 
  rename(ID=i) %>%
  group_by(ID)%>%
  tidybayes::median_qi(logkpred = slogk_pop) %>%
  select(-ID)

results_col <-draws_gen_df %>%
  slice_sample(n=200) %>%
  tidybayes::spread_draws(slogk_col[i]) %>% 
  rename(ID=i) %>%
  group_by(ID)%>%
  tidybayes::median_qi(logkpred = slogk_col) %>%
  select(-ID)

results_ana <-draws_gen_df %>%
  slice_sample(n=200) %>%
  tidybayes::spread_draws(slogk_ana[i]) %>% 
  rename(ID=i) %>%
  group_by(ID)%>%
  tidybayes::median_qi(logkpred = slogk_ana) %>%
  select(-ID)

p1 = data%>%
  cbind(results_ind) %>%
  ggplot(aes(x=logkpred, y=logk, color = as.factor(column))) + 
  geom_point() + 
  #geom_errorbar(aes(xmin = .lower, xmax = .upper), width=0.01)+
  geom_abline(intercept = 0, slope = 1) +
  labs(x = "logk (individual)", y = "logk (observed)") +
  theme(legend.position="none")

p2 = data%>%
  cbind(results_pop) %>%
  ggplot(aes(x=logkpred, y=logk, color = as.factor(column))) + 
  geom_point() + 
  #geom_errorbar(aes(xmin = .lower, xmax = .upper), width=0.01)+
  geom_abline(intercept = 0, slope = 1) +
  labs(x = "logk (population)", y = "logk (observed)") + 
  theme(legend.position="none")

p3= data%>%
  cbind(results_col) %>%
  ggplot(aes(x=logkpred, y=logk, color = as.factor(column))) + 
  geom_point() + 
  #geom_errorbar(aes(xmin = .lower, xmax = .upper), width=0.01)+
  geom_abline(intercept = 0, slope = 1) +
  labs(x = "logk (new-analyte)", y = "logk (observed)") + 
  theme(legend.position="none")


p4= data%>%
  cbind(results_ana) %>%
  ggplot(aes(x=logkpred, y=logk, color = as.factor(column))) + 
  geom_point() + 
  #geom_errorbar(aes(xmin = .lower, xmax = .upper), width=0.01)+
  geom_abline(intercept = 0, slope = 1) +
  labs(x = "logk (new-column)", y = "logk (observed)") + 
  theme(legend.position="none")

concordance_plots<-(p1+p2)/(p3+p4)
concordance_plots
```

## Residual plots
```{r residuals}
data <- data %>% mutate(line=1:n()) 

results_ind <-draws_gen_df %>%
  slice_sample(n=250) %>%
  tidybayes::spread_draws(slogk_ind[line])%>% 
  left_join(data) %>%
  mutate(res = (logk-slogk_ind)/0.02) %>% 
  group_by(line)%>%
  tidybayes::median_qi(residuals = res,
                       logkpred = slogk_ind) %>%
  mutate(residuals = if_else(residuals< -15,-15,residuals))

p1 = data%>%
  left_join(results_ind)  %>%
  ggplot(aes(x=fi, y=residuals, color = as.factor(column))) + 
  geom_point() + 
  #geom_errorbar(aes(xmin = .lower, xmax = .upper), width=0.01)+
  geom_abline(intercept = c(0,-5,5), slope = 0, linetype=2) +
  labs(x = "\u03C6", y = "IWRES") +
  theme(legend.position="none")

p2 = data%>%
  left_join(results_ind)  %>%
  ggplot(aes(x=logkpred, y=residuals, color = as.factor(column))) + 
  geom_point() + 
  #geom_errorbar(aes(xmin = .lower, xmax = .upper), width=0.01)+
  geom_abline(intercept = c(0,-5,5), slope = 0, linetype=2) +
  labs(x = "logk (individual)", y = "IWRES") +
  theme(legend.position="none")

residuals<-p1/p2
residuals
```
##  GOF Plots
### Individual
```{r ind-predictions}
temp_data <-draws_gen_df %>%
  slice_sample(n=500) %>%
  tidybayes::spread_draws(sparam_ind[i,c,..])%>%
  rename(ID=i) %>%
  left_join(analytes_names) %>%
  rename(column=c) %>%
  left_join(column_names) 

plotting_i = function(idx, temp_data, data) {
temp_data%>%
  filter(ID %in% idx) %>%
  tidyr::expand_grid(fi = seq(0,1,0.01)) %>%
  mutate(logk = funlogki_pKa_v102(sparam_ind.1,sparam_ind.2,sparam_ind.3,sparam_ind.4,sparam_ind.5,sparam_ind.6,sparam_ind.7,sparam_ind.8,sparam_ind.9,sparam_ind.10,fi)) %>%
  ggplot(aes(x = fi, y = logk, color = as.factor(column))) +
  ggdist::stat_lineribbon(.width = c(.90), alpha = 1/2) +
  geom_point(data = filter(data,ID %in% idx),aes(x=fi, y=logk, color = as.factor(column))) + 
  facet_wrap(~Column_Phase)+
  labs(title = analytes_names$Compound[idx], x="\u03C6", y="logk (individual)") +
  theme(legend.position = "none") +
  coord_cartesian(xlim=c(0,1),ylim=c(-1,2))
}

plotting_j = function(idx, temp_data, data) {
data_idx<-filter(data,ID %in% idx)
name_map <- unique(data_idx[, c("ID", "Compound")])

temp_data%>%
  filter(ID %in% idx) %>%
  tidyr::expand_grid(fi = seq(0,1,0.01)) %>%
  mutate(logk = funlogki_pKa_v102(sparam_ind.1,sparam_ind.2,sparam_ind.3,sparam_ind.4,sparam_ind.5,sparam_ind.6,sparam_ind.7,sparam_ind.8,sparam_ind.9,sparam_ind.10,fi)) %>%
  ggplot(aes(x = fi, y = logk, color = as.factor(ID))) +
  ggdist::stat_lineribbon(.width = c(.90), alpha = 1/2) +
  geom_point(data = data_idx,aes(x=fi, y=logk, color = as.factor(ID))) + 
  facet_wrap(~Column_Phase)+
  labs(x = expression(varphi), y = expression(logk[obs])) + 
  scale_colour_discrete(labels = name_map$Compound)+
  scale_fill_discrete(guide = "none")+
 # theme(legend.position = "none") +
  coord_cartesian(xlim=c(0,1),ylim=c(-1,2))
}

analytefits_example <- plotting_j(c(24,25,26,42,45,51), temp_data %>% filter(column%in%c(8,12,1,5)), data%>% filter(column%in%c(8,12,1,5)))


analytefits_example
```

```{r setup-plotting}
sink("tabs.qmd")
cat("::: {.panel-tabset}\n\n")
walk(1:nAnalytes, function(x) {
  cat("## Analyte", x, "\n")
  cat("```{r}\n")
  cat("plotting_i(", x, ", temp_data, data)\n", sep = "")
  cat("```\n\n")
})
cat(":::\n")
sink()
```

```{r, child="tabs.qmd"}
```

## Individual level parameters (analyte, column, analyte x column interactions)

Individual parameter are the analyte-specific, column-specific, and analyte x column-specific interaction parameters estimated by the model. The following plots allow to assess the correlations and relationship to predictors for these parameters.

### Individual parameters

```{r iparam}
param <- draws_gen_df %>%
 tidybayes::spread_draws(sparam_ind[i,c,j]) %>%
  group_by(i,c,j)%>%
  summarise(param=mean(sparam_ind)) %>%
  pivot_wider(
    id_cols = c(i, c),
    names_from = j,
    values_from = param
  ) %>%
  left_join(descriptor_df %>%
              select(i=ID,LogP))

p<-param %>%
  rename("logkw" = "1", "S1" = "2", "logS2" = "3") %>%
  ggpairs(columns = c("logkw","S1", "logS2","LogP"), 
  aes(color = as.factor(c)))  +
  theme(
    axis.text.x = element_text(size = 6,angle = 45,hjust = 1,vjust = 1),
    axis.text.y = element_text(size = 6)
  )  

print(p)
```

### etas: analyte effects
```{r ieta}
etas <- draws_gen_df %>%
 tidybayes::spread_draws(seta[i,j]) %>%
  group_by(i,j)%>%
  summarise(eta=mean(seta)) %>%
  pivot_wider(
    id_cols = i,
    names_from = j,
    values_from = eta
  )%>%
  left_join(descriptor_df %>%select(i=ID,LogP)) %>%
  left_join(analytes_df %>%select(i=ID,charge))

etas<-etas %>%
  rename("logkw" = "1", "S1" = "2", "logS2" = "3") %>%
  ggpairs(columns = c("logkw","S1", "logS2", "LogP"),
          aes(color = as.factor(charge))) +
  theme(
    axis.text.x = element_text(size = 6,angle = 45,hjust = 1,vjust = 1),
    axis.text.y = element_text(size = 6)
  )   

etas
```

### kappas: column effects
```{r ikappa}
#| fig-width: 6
#| fig-height: 6
param <- draws_gen_df %>%
 tidybayes::spread_draws(skappa[c,j]) %>%
  group_by(c,j)%>%
  summarise(kappa=mean(skappa)) %>%
  pivot_wider(
    id_cols = c,
    names_from = j,
    values_from = kappa
  ) %>%
  mutate(column=c) %>%
  left_join(column_df) %>%
  mutate(logCL = log10(carbon_loading))

param <- draws_gen_df %>%
 tidybayes::spread_draws(skappa[c,j]) %>%
  group_by(c,j)%>%
  summarise(kappa=mean(skappa)) %>%
  pivot_wider(
    id_cols = c,
    names_from = j,
    values_from = kappa
  ) %>%
  mutate(column=c) %>%
  left_join(column_df) %>%
  mutate(logCL = log10(carbon_loading),
         logPor = log10(`Pore.Size..A.`))

my_scatter <- function(data, mapping, ...){
  ggplot(data = data, mapping = mapping) +
    geom_text(aes(label = c), hjust = 0, vjust = 0, size = 2) +
    scale_x_continuous(expand = expansion(mult = 0.15)) +
    scale_y_continuous(expand = expansion(mult = 0.15)
    )
}

kappas_1<-param %>%
  rename("logkw" = "1","S1" = "2", "logS2" = "3","gamma" = "4", "fid" = "5", "dlogkw" = "6", "dS1" = "7", "dlogS2" = "8") %>%
  ggpairs(columns = c("logkw","S1","logS2", "gamma", "fid", "dlogkw", "dS1", "dlogS2", "logCL","logPor"),
  lower = list(continuous = my_scatter),
  upper = list(continuous = "blank"))  +
  theme(
    axis.text.x = element_text(size = 6,angle = 45,hjust = 1,vjust = 1),
    axis.text.y = element_text(size = 6)
  )   
 
kappas_1
```

```{r ikappa2}
#| fig-width: 6
#| fig-height: 6
param <- draws_gen_df %>%
 tidybayes::spread_draws(logomega_d_pop[c,j]) %>%
  group_by(c,j)%>%
  summarise(logomega_d_pop=mean(logomega_d_pop)) %>%
  pivot_wider(
    id_cols = c,
    names_from = j,
    values_from = logomega_d_pop
  ) %>%
  mutate(column=c) %>%
  left_join(column_df) %>%
  mutate(logCL = log10(carbon_loading),
         logPor = log10(`Pore.Size..A.`))

my_scatter <- function(data, mapping, ...){
  ggplot(data = data, mapping = mapping) +
    geom_text(aes(label = c), hjust = 0, vjust = 0, size = 2) +
    scale_x_continuous(expand = expansion(mult = 0.15)) +
    scale_y_continuous(expand = expansion(mult = 0.15)
    )
}

kappas_2<-param %>%
  rename("logomega_logkw" = "1","logomega_S1" = "2", "logomega_logS2" = "3") %>%
  ggpairs(columns = c("logomega_logkw","logomega_S1","logomega_logS2","logCL","logPor"),
  lower = list(continuous = my_scatter),
  upper = list(continuous = "blank"))  +
  theme(
    axis.text.x = element_text(size = 6,angle = 45,hjust = 1,vjust = 1),
    axis.text.y = element_text(size = 6)
  )  

kappas_2
```

### dzetas: column x analyte interactions
```{r zdzeta}
param <- draws_gen_df %>%
 tidybayes::spread_draws(sdzeta[i,c,j]) %>%
  group_by(i,c,j)%>%
  summarise(sdzeta=mean(sdzeta)) %>%
  pivot_wider(
    id_cols = c(i,c),
    names_from = j,
    values_from = sdzeta
  )%>%
  left_join(descriptor_df %>%select(i=ID,LogP)) %>%
  left_join(analytes_df %>%select(i=ID,charge)) %>%
  rename(column=c) %>%
  left_join(column_names) %>%
  rename("logkw" = "1","S1" = "2","logS2" = "3")%>%
  left_join(column_df %>% select(column, carbon_loading)) %>%
  mutate(logCL = log10(carbon_loading))


param2 <- param %>%
  ungroup() %>%
  select(i, logkw, S1, logS2, Column_Phase) %>%
  pivot_longer(
    cols = c(logkw, S1, logS2),
    names_to = "parameter",
    values_to = "value"
  ) %>% 
  pivot_wider(
    names_from = Column_Phase,
    values_from = value
  )
 
plotting_i<-function(x, param){
p<-param %>%
  filter(Column_Phase %in% x) %>%
  ggpairs(columns = c("logkw", "S1", "logS2", "LogP"),
          title = x,
          aes(color = as.factor(charge), alpha=0.5))+
  theme(
    axis.text.x = element_text(size = 6,angle = 45,hjust = 1,vjust = 1),
    axis.text.y = element_text(size = 6)
  ) 
}

 dzeta_i <- map(unique(param$Column_Phase), \(x) plotting_i(x, param))
 dzeta_i
```

# Manuscript figures
```{r manuscript-figures}
manuscript_figure_dir <- here::here("deliv","figures","manuscript","main")
if(!file.exists(manuscript_figure_dir)) dir.create(manuscript_figure_dir, recursive = T)

supplement_figure_dir <- here::here("deliv","figures","manuscript","supplement")
if(!file.exists(supplement_figure_dir)) dir.create(supplement_figure_dir, recursive = T)

supplement_tables_dir <- here::here("deliv","tables","manuscript","supplement")
if(!file.exists(supplement_tables_dir)) dir.create(supplement_tables_dir, recursive = T)

# Figures
ggsave(here::here(manuscript_figure_dir, "parameter-estimates-1-fig.png"),
       plot=parameter_estimates_1_fig, width = 20, height = 20, units = "cm", dpi = 300)
ggsave(here::here(manuscript_figure_dir, "parameter-estimates-1-fig.pdf"),
       plot=parameter_estimates_1_fig, width = 20, height = 20, units = "cm", dpi = 300)
ggsave(here::here(manuscript_figure_dir, "parameter-estimates-2-fig.png"),
       plot=parameter_estimates_fig, width = 20, height = 20, units = "cm", dpi = 300)
ggsave(here::here(manuscript_figure_dir, "parameter-estimates-2-fig.pdf"),
       plot=parameter_estimates_fig, width = 20, height = 20, units = "cm", dpi = 300)
ggsave(here::here(manuscript_figure_dir, "concordance-plots.png"),
       plot=concordance_plots, width = 20, height = 20, units = "cm", dpi = 300)
ggsave(here::here(manuscript_figure_dir, "concordance-plots.pdf"),
       plot=concordance_plots, width = 20, height = 20, units = "cm", dpi = 300)

ggsave(here::here(supplement_figure_dir, "residuals.png"),
       plot=residuals, width = 20, height = 20, units = "cm", dpi = 300)
ggsave(here::here(supplement_figure_dir, "residuals.pdf"),
       plot=residuals, width = 20, height = 20, units = "cm", dpi = 300)
ggsave(here::here(supplement_figure_dir, "etas.png"),
       plot=etas, width = 20, height = 20, units = "cm", dpi = 300)
ggsave(here::here(supplement_figure_dir, "etas.pdf"),
       plot=etas, width = 20, height = 20, units = "cm", dpi = 300)
ggsave(here::here(supplement_figure_dir, "kappas-1.png"),
       plot=kappas_1, width = 20, height = 20, units = "cm", dpi = 300)
ggsave(here::here(supplement_figure_dir, "kappas-1.pdf"),
       plot=kappas_1, width = 20, height = 20, units = "cm", dpi = 300)
ggsave(here::here(supplement_figure_dir, "kappas-2.png"),
       plot=kappas_2, width = 20, height = 20, units = "cm", dpi = 300)
ggsave(here::here(supplement_figure_dir, "kappas-2.pdf"),
       plot=kappas_2, width = 20, height = 20, units = "cm", dpi = 300)

map(1:13, \(x) ggsave(here::here(supplement_figure_dir, paste0("dzeta-",x,".png")),
       plot=dzeta_i[[x]], width = 20, height = 20, units = "cm", dpi = 300))
map(1:13, \(x) ggsave(here::here(supplement_figure_dir, paste0("dzeta-",x,".pdf")),
       plot=dzeta_i[[x]], width = 20, height = 20, units = "cm", dpi = 300))

ggsave(here::here(supplement_figure_dir, "analyte-fits-example.png"),
       plot=analytefits_example, width = 20, height = 20, units = "cm", dpi = 300)
ggsave(here::here(supplement_figure_dir, "analyte-fits-example.pdf"),
       plot=analytefits_example, width = 20, height = 20, units = "cm", dpi = 300)


#Tables
write.csv(parameter_estimates, file = here(supplement_tables_dir,"parameter-estimates.csv"), row.names = FALSE)

write.csv(parameter_estimates_2, file = here(supplement_tables_dir,"parameter-estimates-kappa.csv"), row.names = FALSE)
write.csv(parameter_estimates_3, file = here(supplement_tables_dir,"parameter-estimates-omegad.csv"), row.names = FALSE)
```



# Session info
```{r}
sessionInfo()
```