---
title: "Simulation"
author:
  - name: "Paweł Wiczling*"
    affiliations:
      - name: "Department of Biopharmaceutics and Pharmacodynamics, Medical University of Gdańsk, Gen. J. Hallera 107, 80-416 Gdańsk, Poland"
date: "`r format(Sys.Date())`"
format:
  html:
    theme: cosmo
    toc: true
    code-fold: true  
    code-tools: true
    fig-width: 7
    fig-height: 7
knitr:
  opts_chunk: 
    dev: "ragg_png"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE, message=FALSE, error=FALSE, warning=FALSE, comment=NA, out.width='95%')
```

# Introductions

A set of simulations exploring possible models and its modification. We illustrate it using the Neue model:

$$
logk(\varphi) = logk_w -  S1 \cdot (1+S2) \cdot \varphi \cdot /(1+S2\cdot \varphi)
$$

# Libraries
```{r library, message=FALSE}
library(ggplot2)
library(gridExtra)
library(patchwork)
library(tidyr)
library(dplyr)
library(purrr)
library(GGally)
library(reshape2)
library(pracma)
library(here)
library(magick)
library(ggcorrplot)

select<-dplyr::select
filter<-dplyr::filter
set.seed(10271998) 
source("helper-functions-v100.R")
```

```{r settings}
data_deriv_dir = here::here("data","deriv")
if(!file.exists(data_deriv_dir)) dir.create(data_deriv_dir, recursive = T)
```


```{r set-theme, include = FALSE}
theme_set(theme_bw())
theme_update(
  axis.title = element_text(size = 10, face = "bold"), 
  axis.text = element_text(size = 8), 
  legend.title = element_blank(),
  legend.text = element_text(size = 8),
  legend.key.size = unit(0.4, "cm"),
  strip.text = element_text(size = 8),
  legend.position = "bottom",
  panel.grid.minor = element_blank()
)
```
# Effect of pH

The changes on organic modifier content change the mobile phase pH and pKa of the analyte. 

```{r pH-effects}
# Parameters
pHo      <- 3.2    
alphapH <- 3
pKa     <- 4 
alphapKA   <- -0.5
logkw1  <- 1
logkw2  <- 2
S11 <- 4
S12 <- 4
S2 <- 2


f_exact <- function(fi) {
  z <- pHo + alphapH * fi - pKa - alphapKA * fi
  k1 = 10^(logkw1 - S11*(1+S2)*fi/(1+S2*fi))
  k2 = 10^(logkw2 - S12*(1+S2)*fi/(1+S2*fi))
  logk = log10((k1 + k2 * 10^(z)) / (1 + 10^(z)))
}

f_1 <- function(fi) {
  logk = logkw1 - S11*(1+S2)*fi/(1+S2*fi)
}

f_2 <- function(fi) {
 logk = logkw2 - S12*(1+S2)*fi/(1+S2*fi)
}

fi_vals <- seq(0, 1, by = 0.01)
df <- data.frame(
  fi = fi_vals,
  partial  = f_exact(fi_vals),
  ionized  = f_1(fi_vals),
  neutral  = f_2(fi_vals)
)

# Long format for ggplot
df_long <- reshape2::melt(df, id.vars = "fi", variable.name = "method", value.name = "value")

# Plot
ggplot(df_long, aes(x = fi, y = value, linetype = method, color = method)) +
  geom_line(size = 1, linewidth = 1, alpha = 0.6) +
  labs(
    x = "fi",
    y = "logk"
  ) 
```

# Empirical dewetting model. Hindge function
```{r dewetting}
# Parameters
fid <- 0.05
delta = 0.001
logkw1  <- 1
S1 <- 4
S2 <- 2

# Function definitions
f_exact <- function(fi) {
   return (logkw1-S1*(1+S2)*fi/(1+S2*fi))
}

# Function definitions
f_dewetting <- function(fi) {

 logko <-logkw1-S1*(1+S2)*fid/(1+S2*fid)
 logki <-logkw1-S1*(1+S2)*fi/(1+S2*fi)

  w <- plogis((fid-fi)/delta)
  
  logk <- w*logko+(1-w)*logki
}

# Data frame
fi_vals <- seq(0, 1, by = 0.01)
df <- data.frame(
  fi = fi_vals,
  nodewetting  = f_exact(fi_vals),
  dewetting  = f_dewetting(fi_vals)
)

# Long format for ggplot
df_long <- reshape2::melt(df, id.vars = "fi", variable.name = "method", value.name = "value")

# Plot
ggplot(df_long, aes(x = fi, y = value, color = method)) +
  geom_line(size = 1) +
  labs(
    x = "fi",
    y = "logk"
  ) 

```

# Empirical silanol model
```{r silanol-model}
# Parameters
## https://www.sciencedirect.com/science/article/pii/S0021967304021879
## Eq. 26

logkw <- 2
logks <- 1
S1 <- 4
S2 <- 2

pKas <- 6

pHo <- 3.2
alpha = 3;

# Function definitions
f_sil <- function(fi) {
   kw = 10^(logkw)
   ks = 10^(logks)
   fix = 10^(-(1+S2)*S1*fi/(1+S2*fi))
   pH = pHo + alpha*fi;
   six = 1/(1+10^(pKas-pH))
   logk = log10(kw*fix + ks*six)
}

# Function definitions
f_org <- function(fi) {
   kw = 10^(logkw)
   fix = 10^(-(1+S2)*S1*fi/(1+S2*fi))
   logk = log10(kw*fix)
}

# Data frame
fi_vals <- seq(0, 1, by = 0.01)
df <- data.frame(
  fi = fi_vals,
  silanols  = f_sil(fi_vals),
  nosilanols  = f_org(fi_vals)
)

# Long format for ggplot
df_long <- reshape2::melt(df, id.vars = "fi", variable.name = "method", value.name = "value")

# Plot
ggplot(df_long, aes(x = fi, y = value, color = method)) +
  geom_line(size = 1) +
  labs(
    x = "fi",
    y = "logk"
  ) 
```

# Combined. Dewetting and simplified silanol model
```{r combined-dewetting-silanol}
fio <-  0.05
delta = 0.001
logkw  <- 2
S1 <- 4
S2 <- 2
logks <- 2
pKas <- 6
pHo <- 3.2
alpha = 2;

# Function definitions
f_exact <- function(fi) {
    kw = 10^(logkw)
    ks = 10^(logks)
    
    pH = pHo + alpha*fi;
    six = 1/(1+10^(pKas-pH))
       
    fix = 10^(-(1+S2)*S1*fi/(1+S2*fi))
    logk = log10(kw*fix + ks*six)
   return(logk)
}

# Function definitions
f_dewetting <- function(fi) {
   kw = 10^(logkw)
   ks = 10^(logks)
   
   fixo = 10^(-(1+S2)*S1*fio/(1+S2*fio))
   sixo = 1/(1+10^(pKas-(pHo + alpha*fio)))
   logko = log10(kw*fixo + ks*sixo)
   
   fix = 10^(-(1+S2)*S1*fi/(1+S2*fi))
   six = 1/(1+10^(pKas-(pHo + alpha*fi)))
   logki = log10(kw*fix + ks*six)
   
   w <- plogis((fid-fi)/delta)
   logk <- w*logko+(1-w)*logki
}

  
fi_vals <- seq(0, 1, by = 0.01)
df <- data.frame(
  fi = fi_vals,
  nodewetting  = f_exact(fi_vals),
  deweting1  = f_dewetting(fi_vals),
  deweting2 = funlogki_sil(logkw, S1, logks, log10(S2), fio, pKas-pHo, alpha, fi_vals)
)

df_long <- reshape2::melt(df, id.vars = "fi", variable.name = "method", value.name = "value")

ggplot(df_long, aes(x = fi, y = value, color = method)) +
  geom_line(size = 1) +
  labs(
    x = "fi",
    y = "logk"
  ) 

```

# Combined. Dewetting and pH effect model

```{r combined-dewetting-pH}
# Parameters
pHo      <- 3.2 
alpha  <- 3
pKa      <- 5.5 
logkw1  <- 1
logkw2  <- 2
S1 <- 4
S2 <- 2
logS2 = log10(S2)
fid <-  0.05
delta = 0.01
logks <- 0.5
pKas <- 6

pKasmpH = pKas-pHo
pHmpKa = pHo-pKa


dlogkw  <- logkw2-logkw1

funlogki_fi <- function(logkw1, S1, logks, S2,
                        pKasmpH, alpha, pHmpKa, dlogkw, fi) {
  
  log10 <- 2.302585092994046  # ln(10)
  
  logfix <- -(1 + S2) * S1 * fi / (1 + S2 * fi)
  
  t1 <- (pKasmpH - alpha * fi) * log10
  t2 <- (pHmpKa  + alpha * fi) * log10
  
  logksfix <- logks - log1p_exp(t1) / log10
  
  a <- (logkw1 - dlogkw + logfix) * log10
  b <- logksfix * log10
  c <- (logkw1 + logfix) * log10 + t2
  
  logk <- log_sum_exp(a, log_sum_exp(b, c)) / log10 -
    log1p_exp(t2) / log10
  
  return(logk)
}

funlogki_pKa <- function(logkw, S1, logks, logS2, fid,
                         pKasmpH, alpha, pHmpKa, dlogkw, fi) {
  
  S2 <- 10^logS2
  delta <- 0.1
  
logkd <- funlogki_fi(
    logkw, S1, logks, S2,
    pKasmpH, alpha, pHmpKa, dlogkw, fid
  )
  
  logk_raw <- funlogki_fi(
    logkw, S1, logks, S2,
    pKasmpH, alpha, pHmpKa, dlogkw, fi
  )
  
  w <- plogis((fid - fi) / 0.01)
  
  logk <- w * logkd + (1 - w) * logk_raw
}

# Function definitions
f_exact <- function(fi) {
  z <-  (pHo + alpha*fi)-(pKa)
  k1 = 10^(logkw1 - S1*(1+S2)*fi/(1+S2*fi))
  k2 = 10^(logkw2 - S1*(1+S2)*fi/(1+S2*fi))
  six = 1/(1+10^(pKas-(pHo+alpha*fi)))
  ks = 10^(logks)
  k1s = k1+ks*six
  logk = log10((k1s + k2 * 10^(z)) / (1 + 10^(z)))
}

f_1 <- function(fi) {
  k1 = 10^(logkw1 - S1*(1+S2)*fi/(1+S2*fi))
  six = 1/(1+10^(pKas-(pHo+alpha*fi)))
  ks = 10^(logks)
  logk = log10(k1+ks*six)
}

f_2 <- function(fi) {
  logk = logkw2 - S1*(1+S2)*fi/(1+S2*fi)
}

f_dewetting <- function(fi) {
 logkd = f_exact(fid)
 logk = f_exact(fi)
  w <- plogis((fid - fi) / 0.01)
  return(w * logkd + (1 - w) * logk)
}

funlogki_pKa_fi <- function(fi_vals) funlogki_pKa(logkw2, S1, logks, logS2, fid,
               pKasmpH, alpha, pHmpKa, dlogkw, fi_vals)


fi_vals <- seq(0, 1, by = 0.01)
df <- data.frame(
  fi = fi_vals,
  partial  = f_exact(fi_vals),
  combined1  = f_dewetting(fi_vals),
  combined2  = funlogki_pKa_fi(fi_vals),

  ionized  = f_1(fi_vals),
  neutral  = f_2(fi_vals)
)

df_long <- reshape2::melt(df, id.vars = "fi", variable.name = "method", value.name = "value")

ggplot(df_long, aes(x = fi, y = value, linetype = method, color = method)) +
  geom_line(size = 1, linewidth = 1, alpha = 0.6) +
  labs(
    x = "fi",
    y = "logk"
  ) 
```
# Combined. Dewetting and pH effect model (empirical)
$$
\begin{aligned}
logk_1 &= logk_{w1} + \gamma \varphi
- \dfrac{(S1_1 \cdot (1+S2_1)\varphi}{1+S2_1\cdot\varphi}, \\[8pt]
logk_2 &= logk_{w2}
- \dfrac{S1_2\cdot(1+S2_2)\cdot\varphi}{1+S2_2\cdot\varphi}, \\[8pt]
logk_t &= \log_{10}\!\left(
\frac{k_1 + k_2\cdot\,10^{(\left(pH_o + \alpha \varphi \right) - pK_a)}}{1 + 10^{(\left(pH_o + \alpha \varphi \right) - pK_a)}}
\right),\\

logk_a &= logk_t(\varphi_{id}), \\
logk_b &= logk_t(\varphi), \\
w &= \frac{1}{1 + \exp\!\left(-\dfrac{\varphi_{id}-\varphi}{0.001}\right)}, \\
logk &= w\cdot\,logk_a + (1-w)\cdot\,logk_b.
\end{aligned}
$$

```{r combined-dewetting-pH-empirical}
# Parameters
pHo      <- 3.2 
alpha  <- 4
pKa      <- 5.5 
logkw1  <- 1
logkw2  <- 2
S1 <- 4
S2 <- 2
logS2 = log10(S2)
fid <-  0.05
pKasmpH = pKas-pHo
pHmpKa = pHo-pKa
dlogkw  <- logkw2-logkw1
cgamma = 4

# Function definitions
f_exact <- function(fi) {
  z <-  (pHo + alpha*fi)-(pKa)
  k1 = 10^(logkw1 + cgamma*fi- S1*(1+S2)*fi/(1+S2*fi))
  k2 = 10^(logkw2 - S1*(1+S2)*fi/(1+S2*fi))
  logk = log10((k1 + k2 * 10^(z)) / (1 + 10^(z)))
}

f_1 <- function(fi) {
  logk = logkw1  + cgamma*fi - S1*(1+S2)*fi/(1+S2*fi)
}

f_2 <- function(fi) {
  logk = logkw2 - S1*(1+S2)*fi/(1+S2*fi)
}

f_dewetting <- function(fi) {
 logkd = f_exact(fid)
 logk = f_exact(fi)
  w <- plogis((fid - fi) / 0.001)
  return(w * logkd + (1 - w) * logk)
}

funlogki_pKa_fi <- function(fi_vals) funlogki_pKa_v102(logkw2, S1, logS2, cgamma, fid,
                              alpha, pHmpKa, -dlogkw, 0, 0, fi_vals)

fi_vals <- seq(0, 1, by = 0.01)
df <- data.frame(
  fi = fi_vals,
#  dewetting3  = f_dewetting(fi_vals),
  combined  = funlogki_pKa_fi(fi_vals),
    ionized  = f_1(fi_vals),
  neutral  = f_2(fi_vals)
)

df_long <- reshape2::melt(df, id.vars = "fi", variable.name = "method", value.name = "value")

fig1<-ggplot(df_long, aes(x = fi, y = value, linetype = method, color = method)) +
  geom_line(size = 1, linewidth = 1, alpha = 0.6) +
  labs(
    x = "fi",
    y = "logk"
  ) 

fig1
```

# Utylity function
$$
\begin{aligned}
d &= \left| \log k_1 - \log k_2 \right|, \\
l_o &= 10^{\min\left(\log k_1,\ \log k_2\right)}, \\
h_i &= 10^{\max\left(\log k_1,\ \log k_2\right)}, \\
U &=
\frac{1}{1 + e^{-(d - 0.07918125)/0.015}}
\times
\frac{1}{1 + e^{-(l_o - 2)/0.25}}
\times
\frac{1}{1 + e^{-(10 - h_i)/1.5}}.
\end{aligned}
$$
```{r utylity-function}
logk1 = seq(0, log10(14), length.out = 50)
logk2 = seq(0, log10(14), length.out = 50)
df <- expand.grid(logk1 = logk1, logk2=logk2)  %>%
 mutate(
    d  = abs(logk1 - logk2),
    lo = 10^(pmin(logk1, logk2)),
    hi = 10^(pmax(logk1, logk2)),
    utylity =
      plogis((d  - 0.07918125) / 0.015) *  # midpoint for selectivity of 1.2, zero for 1.04 and 1 for 1.5
      plogis((lo - 2)      / 0.25)  *
      plogis((10 - hi)     / 1.5)) %>%
  select(-d,-lo,-hi)

fig2<-ggplot(df, aes(x = 10^logk1, y = 10^logk2, z = utylity)) +
  geom_contour_filled()+
   scale_fill_grey(start = 0.9, end = 0.1) +
  labs(x = "Retention factor of analyte 1", y = "Retention factor of analyte 2")+
  scale_x_continuous(limits = c(0, 14), breaks = seq(0, 14, by = 2))+
  scale_y_continuous(limits = c(0, 14), breaks = seq(0, 14, by = 2))
  # geom_vline(xintercept = c(log10(2),log10(10)), linetype = "dotted")+
  # geom_hline(yintercept = c(log10(2),log10(10)), linetype = "dotted")

fig2
```
# Manuscript figures
```{r manuscript-figures}
supplement_figure_dir <- here::here("deliv","figures","manuscript","supplement")
if(!file.exists(supplement_figure_dir)) dir.create(supplement_figure_dir, recursive = T)

# Figures
ggsave(here::here(supplement_figure_dir, "model-sim-1.png"),
       plot=fig1, width = 20, height = 20, units = "cm", dpi = 300)
ggsave(here::here(supplement_figure_dir, "model-sim-1.pdf"),
       plot=fig1, width = 20, height = 20, units = "cm", dpi = 300)

ggsave(here::here(supplement_figure_dir, "utylity-1.png"),
       plot=fig2, width = 20, height = 20, units = "cm", dpi = 300)
ggsave(here::here(supplement_figure_dir, "utylity-1.pdf"),
       plot=fig2, width = 20, height = 20, units = "cm", dpi = 300)
```


# Session info
```{r}
sessionInfo()
```