::: {.panel-tabset}

## Analyte 1 
```{r}
plotting_i(1, temp_data, data)
```

## Analyte 2 
```{r}
plotting_i(2, temp_data, data)
```

## Analyte 3 
```{r}
plotting_i(3, temp_data, data)
```

## Analyte 4 
```{r}
plotting_i(4, temp_data, data)
```

## Analyte 5 
```{r}
plotting_i(5, temp_data, data)
```

## Analyte 6 
```{r}
plotting_i(6, temp_data, data)
```

## Analyte 7 
```{r}
plotting_i(7, temp_data, data)
```

## Analyte 8 
```{r}
plotting_i(8, temp_data, data)
```

## Analyte 9 
```{r}
plotting_i(9, temp_data, data)
```

## Analyte 10 
```{r}
plotting_i(10, temp_data, data)
```

## Analyte 11 
```{r}
plotting_i(11, temp_data, data)
```

## Analyte 12 
```{r}
plotting_i(12, temp_data, data)
```

## Analyte 13 
```{r}
plotting_i(13, temp_data, data)
```

## Analyte 14 
```{r}
plotting_i(14, temp_data, data)
```

## Analyte 15 
```{r}
plotting_i(15, temp_data, data)
```

## Analyte 16 
```{r}
plotting_i(16, temp_data, data)
```

## Analyte 17 
```{r}
plotting_i(17, temp_data, data)
```

## Analyte 18 
```{r}
plotting_i(18, temp_data, data)
```

## Analyte 19 
```{r}
plotting_i(19, temp_data, data)
```

## Analyte 20 
```{r}
plotting_i(20, temp_data, data)
```

## Analyte 21 
```{r}
plotting_i(21, temp_data, data)
```

## Analyte 22 
```{r}
plotting_i(22, temp_data, data)
```

## Analyte 23 
```{r}
plotting_i(23, temp_data, data)
```

## Analyte 24 
```{r}
plotting_i(24, temp_data, data)
```

## Analyte 25 
```{r}
plotting_i(25, temp_data, data)
```

## Analyte 26 
```{r}
plotting_i(26, temp_data, data)
```

## Analyte 27 
```{r}
plotting_i(27, temp_data, data)
```

## Analyte 28 
```{r}
plotting_i(28, temp_data, data)
```

## Analyte 29 
```{r}
plotting_i(29, temp_data, data)
```

## Analyte 30 
```{r}
plotting_i(30, temp_data, data)
```

## Analyte 31 
```{r}
plotting_i(31, temp_data, data)
```

## Analyte 32 
```{r}
plotting_i(32, temp_data, data)
```

## Analyte 33 
```{r}
plotting_i(33, temp_data, data)
```

## Analyte 34 
```{r}
plotting_i(34, temp_data, data)
```

## Analyte 35 
```{r}
plotting_i(35, temp_data, data)
```

## Analyte 36 
```{r}
plotting_i(36, temp_data, data)
```

## Analyte 37 
```{r}
plotting_i(37, temp_data, data)
```

## Analyte 38 
```{r}
plotting_i(38, temp_data, data)
```

## Analyte 39 
```{r}
plotting_i(39, temp_data, data)
```

## Analyte 40 
```{r}
plotting_i(40, temp_data, data)
```

## Analyte 41 
```{r}
plotting_i(41, temp_data, data)
```

## Analyte 42 
```{r}
plotting_i(42, temp_data, data)
```

## Analyte 43 
```{r}
plotting_i(43, temp_data, data)
```

## Analyte 44 
```{r}
plotting_i(44, temp_data, data)
```

## Analyte 45 
```{r}
plotting_i(45, temp_data, data)
```

## Analyte 46 
```{r}
plotting_i(46, temp_data, data)
```

## Analyte 47 
```{r}
plotting_i(47, temp_data, data)
```

## Analyte 48 
```{r}
plotting_i(48, temp_data, data)
```

## Analyte 49 
```{r}
plotting_i(49, temp_data, data)
```

## Analyte 50 
```{r}
plotting_i(50, temp_data, data)
```

## Analyte 51 
```{r}
plotting_i(51, temp_data, data)
```

## Analyte 52 
```{r}
plotting_i(52, temp_data, data)
```

## Analyte 53 
```{r}
plotting_i(53, temp_data, data)
```

## Analyte 54 
```{r}
plotting_i(54, temp_data, data)
```

## Analyte 55 
```{r}
plotting_i(55, temp_data, data)
```

## Analyte 56 
```{r}
plotting_i(56, temp_data, data)
```

## Analyte 57 
```{r}
plotting_i(57, temp_data, data)
```

## Analyte 58 
```{r}
plotting_i(58, temp_data, data)
```

## Analyte 59 
```{r}
plotting_i(59, temp_data, data)
```

## Analyte 60 
```{r}
plotting_i(60, temp_data, data)
```

## Analyte 61 
```{r}
plotting_i(61, temp_data, data)
```

## Analyte 62 
```{r}
plotting_i(62, temp_data, data)
```

## Analyte 63 
```{r}
plotting_i(63, temp_data, data)
```

## Analyte 64 
```{r}
plotting_i(64, temp_data, data)
```

## Analyte 65 
```{r}
plotting_i(65, temp_data, data)
```

## Analyte 66 
```{r}
plotting_i(66, temp_data, data)
```

## Analyte 67 
```{r}
plotting_i(67, temp_data, data)
```

## Analyte 68 
```{r}
plotting_i(68, temp_data, data)
```

## Analyte 69 
```{r}
plotting_i(69, temp_data, data)
```

## Analyte 70 
```{r}
plotting_i(70, temp_data, data)
```

## Analyte 71 
```{r}
plotting_i(71, temp_data, data)
```

## Analyte 72 
```{r}
plotting_i(72, temp_data, data)
```

## Analyte 73 
```{r}
plotting_i(73, temp_data, data)
```

## Analyte 74 
```{r}
plotting_i(74, temp_data, data)
```

## Analyte 75 
```{r}
plotting_i(75, temp_data, data)
```

## Analyte 76 
```{r}
plotting_i(76, temp_data, data)
```

## Analyte 77 
```{r}
plotting_i(77, temp_data, data)
```

## Analyte 78 
```{r}
plotting_i(78, temp_data, data)
```

## Analyte 79 
```{r}
plotting_i(79, temp_data, data)
```

## Analyte 80 
```{r}
plotting_i(80, temp_data, data)
```

## Analyte 81 
```{r}
plotting_i(81, temp_data, data)
```

## Analyte 82 
```{r}
plotting_i(82, temp_data, data)
```

## Analyte 83 
```{r}
plotting_i(83, temp_data, data)
```

## Analyte 84 
```{r}
plotting_i(84, temp_data, data)
```

## Analyte 85 
```{r}
plotting_i(85, temp_data, data)
```

## Analyte 86 
```{r}
plotting_i(86, temp_data, data)
```

## Analyte 87 
```{r}
plotting_i(87, temp_data, data)
```

:::
